### 2018-06-17 paper/ms.tex
start paper

\documentclass[aps,prd,reprint,nofootinbib, superscriptaddress]{revtex4-1}
\usepackage{amsmath,amssymb, amsthm,amstext}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{array, enumerate}
\usepackage{bm}
\usepackage{multirow}
\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}

% Shorts
\def\nn{\nonumber}
\def\st{\sin\theta}
\def\ct{\cos\theta}
\def\sst{\sin^2\theta}
\def\cct{\cos^2\theta}
\def\Ap{A_\phi}
\def\Ar{A_{\phi,r}}
\def\Arr{A_{\phi,rr}}
\def\Am{A_{\phi,\mu}}
\def\Amm{A_{\phi,\mu\mu}}
\def\Ah{A_{\phi,\theta}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ben{\begin{eqnarray}}
\def\een{\end{eqnarray}}
\def\WH{\Omega_{\rm H}}
\def\e{{\bf e}}
\def\AHE{A_\phi^{\rm HE}}
\def\AEE{A_\phi^{\rm EE}}

\def\Alfven{Alfv\`en}

\begin{document}
\title{The force-free magnetosphere of a Kerr black hole: the role of boundary conditions}
\author{Zhen Pan}
\email{zhpan@ucdavis.edu}
\affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario N2L 2Y5, Canada}

\date{\today}

\begin{abstract}
    xx
\end{abstract}

\maketitle

\section{Introduction}

\section{basic equations}
\label{sec:basic}
In this paper, we adopt the Kerr-Schild
coordinate with the line element
\[
\begin{aligned}
ds^2 =
&-\left( 1-\frac{2r}{\Sigma} \right)dt^2 + \left( \frac{4
r}{\Sigma} \right) dr dt + \left(1+\frac{2r}{\Sigma} \right) dr^2 \\
&+ \Sigma d\theta^2 - \frac{4 a r \sin^2\theta}{\Sigma} d\phi dt
- 2 a \left(1+\frac{2r}{\Sigma}\right) \sin^2\theta d\phi dr     \\
& + \frac{\beta}{\Sigma} \sst d\phi^2
\end{aligned}
\]
where $\Sigma = r^2 + a^2 \mu^2$, $\Delta = r^2 -2r + a^2$,
$\beta = \Delta\Sigma + 2r(r^2 + a^2)$, and $a$ is the dimensionless BH spin.
In the force-free approximation, electromagnetic energy greatly exceeds that of matter.
Consequently, the force-free magnetospheres is governed by energy
conservation equation of electromagnetic field, or
conventionally called as the GS equation.
In the Kerr spacetime,
the axisymmetric and steady GS equation can be written in a compact form \cite{Pan2017}
\ben
\label{eq:GSg}
&&\phantom{+}
 \left[\Arr + \frac{\sst}{\Delta}\Amm \right]  \mathcal K(r,\theta; \Omega )\nn \\
&&
+\left[\Ar \partial_r^\Omega  +  \frac{\sst}{\Delta}\Am \partial_\mu^\Omega\right] \mathcal K(r,\theta; \Omega ) \nn \\
&&
+ \frac{1}{2}\left[\Ar^2 + \frac{\sst}{\Delta}\Am^2\right]  \Omega' \partial_\Omega \mathcal K(r,\theta; \Omega )\nn \\
&&
- \frac{\Sigma}{\Delta}II' = 0 \ ,
\een
with $\mathcal K(r,\theta; \Omega )= \left[\frac{\beta}{\Sigma}\Omega^2 \sst
-\frac{4ra}{\Sigma}\Omega \sst
-\left(1-\frac{2r}{\Sigma}\right)\right]$ being the LS function,
$\mu\equiv\ct$,  and  the primes designate  derivatives with respect to $A_\phi$.
$\partial_i^\Omega (i=r, \mu)$  denotes the partial derivative
with respect to coordinate $i$ with $\Omega$ fixed, and $\partial_\Omega$ is the derivative with
respect to $\Omega$.

\section{Uniform field solution}

\subsection{Boundary conditions}

\begin{subequations}
\begin{align}
    A_\phi(\mu = 1) &= 0,  \label{eq:bc1}\\
    \Am(\mu = 0, r > 2) &= 0, \label{eq:bc2}\\
    B^2-E^2 (\mu = 0, r_+ \leq r \leq 2) &=0.\label{eq:bc3}
\end{align}
\end{subequations}

where
\be
\begin{aligned}
B^2-E^2 &= \frac{1}{\Sigma \sst} \left[ -\mathcal{K} \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right]\\
B^2+E^2 &= \frac{1}{\Sigma \sst} \left[ \left(\mathcal{K}+\frac{\Delta\Sigma}{\beta} \right) \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right]\\
\end{aligned}
\ee
\be
\label{eq:nbc}
\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Big/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
\ee
where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.

\subsection{Numerical method}
We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition
\be I = 2\Omega A_\phi, \label{eq:rad}\ee
and suitable $\Am(\mu =0, r_+\leq r \leq 2)$
enabling the boundary condition (\ref{eq:bc3}).

1. We choose an initial guess for the field configuration, $\Omega(\Ap)$ and equator boundary condition as follows
\begin{subequations}
\begin{align}
    \Ap &= r^2 \sst,  \label{eq:gss1} \\
    \Omega & = 0.5\WH\left(1-\Ap/\AHE\right), \label{eq:gss2}\\
    \Am(\mu =0, r_+\leq r \leq 2) & = -1\times (r/r_+)^3. \label{eq:gss3}
\end{align}
\end{subequations}

2. We evolve the GS equation and find $II'$ enabling smooth field lines across the LS
\cite[see][for details]{Contopoulos2013, Nathanail2014, Pan2016a}.

3. Usually the current $I$ found in Step 2 neither satisfies the radiation condition (\ref{eq:rad})
nor enables the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
$\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
\be
 A_{\phi,\mu\rm new}  = A_{\phi,\mu \rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
\ee
enabling the radiation condition (\ref{eq:rad}) for
$A_\phi\in [A_\phi^{\rm HE}, A_\phi^{\rm EE}]$, where $\zeta_1$ is an
empirical step size.

4. The final step is to adjust  $\Omega(\Ap < \AHE)$ enabling  the radiation condition (\ref{eq:rad})
 for $A_\phi < A_\phi^{\rm HE}$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
 enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in [\AHE, \AEE]$.
 The first part is straightforward, i.e.,
 \be
\Omega_{\rm new}(\Ap < \AHE) = \frac{I}{2\Ap},
 \ee
 and the second part can be realized by
 \be
\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Big|_{\mu=0, r_+\leq r \leq 2}
 \ee
 where $\zeta_2$ is again an empirical step size, and we have multiplied factor $\Delta$
 to avoid numerical difficulty in the vicinity of the event horizon. To avoid unphysical discontinuity in the angular
 velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ via a fifth-order polynomial.

 5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat step 2 to step 4,
 until the numerical prescription (\ref{eq:nbc}) is satisfied.

\begin{figure}
\includegraphics[scale=0.55]{f1}
\caption{\label{fig:field_lines} The configuration of field lines for the magnetosphere of a Kerr BH with spin $a=0.99$,
where the solid/red line is the ergosphere and the dashed/black line is the LS, both of which intersect with
the equator at $r=2 M$. }
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{f2}
\caption{\label{fig:omega} $a=0.99$}
\end{figure}

\bibliography{ms}

\end{document}

### 2018-06-17 scripts/func.jl

@@ -214,7 +214,7 @@ function Rμ2xy(crd, U, ils; xmax = 3., ymax = 4., len = 1024, Umax = 9.0, cnum 
     xhz = sqrt(rhz^2 - yhz.^2)
 
     levels = linspace(0.005, Umax, cnum)
-    figure(figsize=(5,6))
+    figure(figsize=(5, 6))
     contour(Uxy, levels, extent = (0, xmax, 0, ymax), colors = "k")
     plot(xIRS, yIRS, "r-")
     plot(xILS, yILS,  "k--")

### 2018-06-17 scripts/run.jl

@@ -71,35 +71,52 @@ include("func.jl")
 @load "/home/zhenpan/Astroph/Uniform_Sol/a99.jld"
 
 Ubm = linspace(0., U_H, 64)
-fig = figure(figsize=(8,10))
-subplot(311)
-plot(Ubm/U_H, Ω_I.Ωspl(Ubm)/crd.Ω_H, lw = 2, "k")
-plot(Ubm/U_H, 0.5*(1-Ubm/U_H), lw = 2, "r--")
+fig = figure(figsize=(5, 3.6))
+plot(Ubm, Ω_I.Ωspl(Ubm)/crd.Ω_H, lw = 2, "k")
+plot(Ubm, 0.5*(1-Ubm/U_H), lw = 2, "r--")
 ylim(0., 0.52)
+xlabel(L"$A_\phi$", fontsize = 20)
 ylabel(L"$\Omega/ \Omega_{\rm H}$", fontsize = 20)
-tick_params(axis="both", which="major", labelsize=14)
+tick_params(axis="both", which="major", length =4, labelsize=14)
 ax = gca()
+mx = matplotlib[:ticker][:MultipleLocator](0.5)
 My = matplotlib[:ticker][:MultipleLocator](0.1) # Define interval of major ticks
+my = matplotlib[:ticker][:MultipleLocator](0.05)
+ax[:xaxis][:set_minor_locator](mx)
 ax[:yaxis][:set_major_locator](My)
-
-subplot(312)
-plot(Ubm/U_H, Ω_I.IIpspl(Ubm)/(crd.Ω_H*U_H), lw = 2, "k")
-ylim(-0.07, 0.062)
-ylabel(L"$II'/ (\Omega_{\rm H}A_\phi^{\rm H})$", fontsize = 20)
-tick_params(axis="both", which="major", labelsize=14)
-bx = gca()
-My = matplotlib[:ticker][:MultipleLocator](0.03) # Define interval of major ticks
-bx[:yaxis][:set_major_locator](My)
-
-subplot(313)
-plot(Ubm/U_H, 2*Ω_I.Ωspl(Ubm).*Ubm/(crd.Ω_H*U_H), lw = 2, "k")
-ylim(0., 0.32)
-xlabel(L"$A_\phi/ A_\phi^{\rm H}$", fontsize = 20)
-ylabel(L"$I/ (\Omega_{\rm H}A_\phi^{\rm H})$", fontsize = 20)
-tick_params(axis="both", which="major",labelsize=14)
-cx = gca()
[…]

### 2018-06-17 paper/ms.tex
abs save

@@
 \begin{abstract}
-    xx
+    The role of boundary conditions in the structure of
+    a force-free black hole magnetosphere was rarely discussed, since previous studies have been focused on the
+    the field lines entering the horizon which is causally disconnected and on which the boundary
+    condition imposed usually makes no difference to the magnetosphere structure. However,
+    recent high-resolution general relativistic (GR) force-free simulation shows that there are both
+    field lines entering the horizon and field lines ending up on the equatorial current sheet
+    within the ergosphere for asymptotic uniform field. For the latter, the equatorial boundary
+    condition is well approximated being marginally force-free, i.e., $B^2-E^2=0$, where $B$ and
+    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit this
+    problem by solving the GR Grad-Shafranov equation which governs the structure of
+    the force-free magnetosphere in steady state and self-consistently imposing the marginally force-free equatorial
+    condition. We also discuss the applicability of this boundary condition and the numerical algorithm proposed
+    in this paper for general magnetic field configurations.
 \end{abstract}
@@
 \be I = 2\Omega A_\phi, \label{eq:rad}\ee
-and suitable $\Am(\mu =0, r_+\leq r \leq 2)$
-enabling the boundary condition (\ref{eq:bc3}).
+enabling field lines smoothly crossing the LS,
+and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
+guaranteeing the boundary condition (\ref{eq:bc3}).
 
-1. We choose an initial guess for the field configuration, $\Omega(\Ap)$ and equator boundary condition as follows
+In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
+computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
+and implement a uniform $512\times 64$ grid. The detailed algorithm is listed as follows.
+
+1. We choose an initial guess for the field configuration, $\Omega(\Ap)$, $I(\Ap)$
+and equator boundary condition as follows
 \begin{subequations}
@@
     \Omega & = 0.5\WH\left(1-\Ap/\AHE\right),  \label{eq:gss2}\\
-    \Am(\mu =0, r_+\leq r \leq 2) & = -1\times (r/r_+)^3. \label{eq:gss3}
+    I & = \WH \Ap\left(1-\Ap/\AHE\right) , \\
+    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3. \label{eq:gss3}
 \end{align}
@@
 
-2. We evolve the GS equation and find $II'$ enabling smooth field lines across the LS
-\cite[see][for details]{Contopoulos2013, Nathanail2014, Pan2016a}.
+2. We evolve the GS equation (\ref{eq:GSg}) and adjust $II'(\Ap)$ enabling smooth field lines across the LS
+\cite[see e.g.][for details]{Contopoulos2013, Nathanail2014, Pan2016a, Mahlmann2018}.
 
 3. Usually the current $I$ found in Step 2 neither satisfies the radiation condition (\ref{eq:rad})
-nor enables the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
+nor guarantees the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
 $\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
 \be
- A_{\phi,\mu\rm new}  = A_{\phi,\mu \rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
+ A_{\phi,\mu}|_{\rm new}  = A_{\phi,\mu}|_{\rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
 \ee
@@
 
-4. The final step is to adjust  $\Omega(\Ap < \AHE)$ enabling  the radiation condition (\ref{eq:rad})
- for $A_\phi < A_\phi^{\rm HE}$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
+4. The remaining task is to adjust  $\Omega(0< \Ap < \AHE)$ enabling  the radiation condition (\ref{eq:rad})
+ for $A_\phi \in (0, A_\phi^{\rm HE})$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
  enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in [\AHE, \AEE]$.
@@
  \be
-\Omega_{\rm new}(\Ap < \AHE) = \frac{I}{2\Ap},
+\Omega_{\rm new} = \frac{I}{2\Ap}\Bigg|_{0 < \Ap < \AHE},
  \ee
@@
  \be
-\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Big|_{\mu=0, r_+\leq r \leq 2}
+\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Bigg|_{\mu=0, r_+\leq r \leq 2},
  \ee
  where $\zeta_2$ is again an empirical step size, and we have multiplied factor $\Delta$
- to avoid numerical difficulty in the vicinity of the event horizon. To avoid unphysical discontinuity in the angular
- velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ via a fifth-order polynomial.
+ in the correction term to avoid numerical difficulty in the vicinity of the event horizon.
+ To eliminate unphysical discontinuity in the angular
+ velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ on the whole range
+ $[0, \AEE]$ via a fifth-order polynomial.
 
  5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat step 2 to step 4,
- until the numerical prescription (\ref{eq:nbc}) is satisfied.
+ until the numerical prescription (\ref{eq:nbc}) for the boundary condition (\ref{eq:bc3}) is satisfied.
 

### 2018-06-17 paper/ms.tex
state save

@@
 
+The boundary conditions on the polar axis, on the horizon and at infinity are natural.
+
 \begin{subequations}
@@
 \end{subequations}
+where $r_+$ is the radius of the event horizon.
 
-where
+In our computation, we use following numerical prescription
+\be
+\label{eq:nbc}
+\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Big/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
+\ee
+as a proxy of the marginally force-free equatorial boundary condition (\ref{eq:bc3}),
+where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.
+Specifically,
 \be
@@
 \ee
-\be
-\label{eq:nbc}
-\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Big/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
-\ee
-where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.
+where $B^2+E^2$ is the energy density measured by the zero-angular-momentum-observers.
 
@@
     I & = \WH \Ap\left(1-\Ap/\AHE\right) , \\
-    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3. \label{eq:gss3}
+    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3, \label{eq:gss3}
 \end{align}
 \end{subequations}
+where $\WH = a/2r_+$ is the BH angular velocity.
 
@@
 
+\subsection{Numerical results}
+
+In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
+which displays two generic features: 1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
+2) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
+both of which carry electric current and therefore Poynting flux.
+
 \begin{figure}
@@
 
+\section{Comparison with previous studies}
+
+\section{Summary and Discussions}
+
 \bibliography{ms}

### 2018-06-17 paper/ms.tex
state save

@@
 \be I = 2\Omega A_\phi, \label{eq:rad}\ee
-enabling field lines smoothly crossing the LS,
+and enabling field lines smoothly crossing the LS,
 and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
@@
 
- 5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat step 2 to step 4,
+ 5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat Step 2 to Step 4,
  until the numerical prescription (\ref{eq:nbc}) for the boundary condition (\ref{eq:bc3}) is satisfied.
@@
 \includegraphics[scale=0.6]{f2}
-\caption{\label{fig:omega} $a=0.99$}
+\caption{\label{fig:omega} Solid: the angular velocity function $\Omega(\Ap)$ for $a=0.99$.
+Dashed: a linear function for comparison.}
 \end{figure}

### 2018-06-20 paper/ms.tex
state save

@@
 
-The boundary conditions on the polar axis, on the horizon and at infinity are natural.
-
+The boundary conditions
 \begin{subequations}
@@
 \subsection{Numerical method}
-We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition
+We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ connected by the radiation condition
 \be I = 2\Omega A_\phi, \label{eq:rad}\ee
@@
 computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
-and implement a uniform $512\times 64$ grid. The detailed algorithm is listed as follows.
+and implement a uniform $512\times 64$ grid. The detailed algorithm is clarified
+in the following steps.
 
-1. We choose an initial guess for the field configuration, $\Omega(\Ap)$, $I(\Ap)$
-and equator boundary condition as follows
+1. We choose an initial guess for the field configuration, functions
+$\{ \Omega(\Ap), I(\Ap)\}$
+and equatorial boundary condition as follows
 \begin{subequations}
@@
 \end{subequations}
-where $\WH = a/2r_+$ is the BH angular velocity.
+where $\WH = a/2r_+$ is the angular velocity of the BH.
 
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-which displays two generic features: 1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
-2) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
+which displays three generic features: (1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
+(2) there is no current sheet within the magnetosphere except the equatorial current sheet extending from $r_+$ to $2M$,
+which gives rise to a cusp to the magnetic field lines,
+(3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
 both of which carry electric current and therefore Poynting flux.
@@
 
+\subsection{Solution uniqueness}
+
+\subsection{Topology of near-horizon field lines}
+
 \section{Summary and Discussions}

### 2018-06-21 scripts/run.jl
state save

@@ -1,9 +1,9 @@
 using PyPlot
-include("GS.jl")
-include("SOR.jl")
-include("func.jl")
+include("scripts/GS.jl")
+include("scripts/SOR.jl")
+include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 3.0)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 3.2)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
@@ -15,7 +15,7 @@ bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 0)  # 0:init, else:updater
 
 Ωpar_loop = 1; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 15) & (fsq2_avg > 1.e-4)
+while (Ωpar_loop <= 20) & (fsq2_avg > 1.e-4)
     for BCloop = 1:20
         for Ωloop = 1:200
             for Iloop = 1:5
@@ -59,7 +59,7 @@ plot(Ueqt, fsq, lw = 2)
 plot(Ueqt, zeros(Ueqt), "--")
 
 using JLD
-@save "/home/zhenpan/Astroph/Uniform_Sol/a99.jld" crd mtr Ω_par U Ω_I U_H grd ils Ueqt fsq fsq2_avg
+@save "/home/zhenpan/Astroph/Uniform_Sol/scripts/a99.jld" crd mtr Ω_par U Ω_I U_H grd ils Ueqt fsq fsq2_avg
 #@save "/home/zhenpan/Astroph/Uniform_Sol/a998.jld" crd mtr Ω_par U Ω_I U_H grd ils Ueqt fsq fsq2_avg
 
 using JLD

### 2018-06-21 plot.jl
state save

@@ -1,0 +1,27 @@
+using PyPlot
+using JLD
+include("scripts/GS.jl")
+include("scripts/SOR.jl")
+include("scripts/func.jl")
+
+Ω_sim = readdlm("/home/zhenpan/Astroph/Uniform_Sol/psi_omegaf_a_0.990.out")
+@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a99.jld"
+
+Ubm = linspace(0., U_H, 64)
+fig = figure(figsize=(5, 3.6))
+plot(Ubm/U_H, Ω_I.Ωspl(Ubm)/crd.Ω_H, lw = 2, "k")
+plot(Ubm/U_H, 0.5*(1-Ubm/U_H), lw = 2, "r--")
+plot(Ω_sim[:,1]/Ω_sim[end,1], Ω_sim[:,2], lw = 2)
+ylim(0., 0.52)
+xlabel(L"$A_\phi$", fontsize = 20)
+ylabel(L"$\Omega/ \Omega_{\rm H}$", fontsize = 20)
+tick_params(axis="both", which="major", length =4, labelsize=14)
+ax = gca()
+mx = matplotlib[:ticker][:MultipleLocator](0.2)
+My = matplotlib[:ticker][:MultipleLocator](0.1) # Define interval of major ticks
+my = matplotlib[:ticker][:MultipleLocator](0.05)
+ax[:xaxis][:set_minor_locator](mx)
+ax[:yaxis][:set_major_locator](My)
+ax[:yaxis][:set_minor_locator](my)
+tight_layout()
+savefig("f2.pdf")

### 2018-06-21 scripts/func.jl

@@ -116,11 +116,16 @@ function Ω_fnc(Ω_H::Float64, Ω_par::Array{Float64}, xcol::Array{Float64})
 end
 
 function Ωpar_updater!(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I, ils::LS; Isf = 0.02)
-    Ueqt, B2mE2, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
-    B2mE2_spl = Spline1D(Ueqt, B2mE2, bc="zero")
+    # Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
+    # B2mE2_spl = Spline1D(Ueqt, B2mE2, bc="zero")
+    # Ucol = ils.ULS; U_H =  Ucol[1]
+    # Iexp = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*B2mE2_spl(Ucol)   # 2Ωψ + (B2-E2) correction
 
+    Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
+    Icrt_spl  = Spline1D(Ueqt, B2mE2-B2mE2_exp)
     Ucol = ils.ULS; U_H =  Ucol[1]
-    Iexp = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*B2mE2_spl(Ucol)   # 2Ωψ + (B2-E2) correction
+    Iexp = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt_spl(Ucol)
+
     Inum = Ω_I.Ispl(Ucol)
     Inew = Inum.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1]) +  Iexp.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1])
 
@@ -227,7 +232,7 @@ end
 
 function Fsq(U::Array{Float64, 2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I)
     idx = crd.idx_r2
-    ∂1U = (U[1, 2:idx+1] - U[1, 1:idx]) ./ crd.δR
+    ∂1U = zeros(idx);  ∂1U[2:idx] = (U[1, 2:idx] - U[1, 1:idx-1]) ./ crd.δR
[…]

### 2018-06-21 scripts/run.jl

@@ -1,29 +1,29 @@
 using PyPlot
+using JLD
 include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 3.2)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 3.5)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
 grd      = Grid(crd, mtr, Ω_I)
 ils      = LS(U, grd, crd, Ω_I)
 lsn      = LS_neighbors(U, ils, grd, crd)
-δU       = zeros(crd.μlen); Res = 0.
 bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 0)  # 0:init, else:updater
 
+δU        = zeros(crd.μlen); Res = 0.
 Ωpar_loop = 1; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 20) & (fsq2_avg > 1.e-4)
-    for BCloop = 1:20
-        for Ωloop = 1:200
+while (Ωpar_loop <= 10) & (fsq2_avg > 1.e-4)
+    for BCloop = 1:15
+        for Ωloop = 1:150
             for Iloop = 1:5
                 U,  Res, dU = Solver!(U, crd, grd, Ω_I, ils, lsn, maxitr = 2, omega = 1.0)
                 U, U_H      = Bounds!(U, crd, Ω_I, lsn, bc_eqt)                  #where bc_eqt contains ∂μU on equator
                 ils,Ω_I, δU = IIp_updater!(U, crd, Ω_I, ils, lsn, Isf = 0.08)    #update IIp in ils and Ω_I
                 grd         = Grid!(grd, crd, mtr, Ω_I)                          #update IIp in grd
-                #println("(BCloop, Ωloop, Iloop) = ($BCloop $Ωloop $Iloop), res = $(sum(abs(Res))), U_H = $U_H, U_he = $(U[1,1])")
             end
[…]

### 2018-06-22 plot.jl
state save

@@ -5,7 +5,7 @@ include("scripts/SOR.jl")
 include("scripts/func.jl")
 
 Ω_sim = readdlm("/home/zhenpan/Astroph/Uniform_Sol/psi_omegaf_a_0.990.out")
-@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a99.jld"
+@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a99_Icrt.jld"
 
 Ubm = linspace(0., U_H, 64)
 fig = figure(figsize=(5, 3.6))
@@ -24,4 +24,4 @@ ax[:xaxis][:set_minor_locator](mx)
 ax[:yaxis][:set_major_locator](My)
 ax[:yaxis][:set_minor_locator](my)
 tight_layout()
-savefig("f2.pdf")
+savefig("f2b.pdf")

### 2018-06-22 scripts/func.jl

@@ -116,42 +116,23 @@ function Ω_fnc(Ω_H::Float64, Ω_par::Array{Float64}, xcol::Array{Float64})
 end
 
 function Ωpar_updater!(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I, ils::LS; Isf = 0.02)
-    # Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
-    # B2mE2_spl = Spline1D(Ueqt, B2mE2, bc="zero")
-    # Ucol = ils.ULS; U_H =  Ucol[1]
-    # Iexp = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*B2mE2_spl(Ucol)   # 2Ωψ + (B2-E2) correction
+    Ucol = reverse(ils.ULS); U_H =  Ucol[end]
 
     Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
-    Icrt_spl  = Spline1D(Ueqt, B2mE2-B2mE2_exp)
-    Ucol = ils.ULS; U_H =  Ucol[1]
-    Iexp = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt_spl(Ucol)
-
-    Inum = Ω_I.Ispl(Ucol)
-    Inew = Inum.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1]) +  Iexp.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1])
+    Icrt2_spl  = Spline1D(Ueqt, B2mE2-B2mE2_exp, bc="zero")
+    I_eqt = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt2_spl(Ucol)
+    #Icrt1 = Ω_I.Ispl(Ucol) - 2*Ω_I.Ωspl(Ucol).*Ucol
+    #I_hrz = 2*Ω_I.Ωspl(Ucol).*Ucol + Isf*Icrt
+    I_hrz = Ω_I.Ispl(Ucol)
+    I_new = I_hrz.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1]) + I_eqt.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1])
 
     xcol = Ucol/U_H;  Ω_H  = crd.Ω_H
-
[…]

### 2018-06-22 scripts/run.jl

@@ -4,7 +4,7 @@ include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 3.5)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 4.0)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
@@ -16,7 +16,7 @@ bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 0)  # 0:init, else:updater
 δU        = zeros(crd.μlen); Res = 0.
 Ωpar_loop = 1; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 10) & (fsq2_avg > 1.e-4)
+while (Ωpar_loop <= 5) & (fsq2_avg > 1.e-4)
     for BCloop = 1:15
         for Ωloop = 1:150
             for Iloop = 1:5

### 2018-06-23 scripts/SOR.jl
state save

@@ -66,7 +66,7 @@ function Bounds!(U::Array{Float64,2}, crd::Cord, Ω_I::Ω_and_I, lsn::LS_neighbo
     return U, U_H
 end
 
-function BC_gen(U::Array{Float64,2}, crd::Cord, Ω_I::Ω_and_I; BC_opt = 0, Isf = 5.)
+function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_opt = 0, Isf = 5.)
     idx_r2  = crd.idx_r2
     idx_bd  = crd.idx_xbd[1]
     rmin    = crd.rmin
@@ -86,7 +86,11 @@ function BC_gen(U::Array{Float64,2}, crd::Cord, Ω_I::Ω_and_I; BC_opt = 0, Isf 
         iip  = Ispl(Ucol).*derivative(Ispl, Ucol)
         IIp  = Ω_I.IIpspl(Ucol)
 
-        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip)
+        #∂μU_zj = Ispl(Ucol[1])*crd.rmin/2./(Ω_I.Ωspl(Ucol[1])-crd.Ω_H)
+
+        Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
+
+        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip) - 0.04*(1.-rcol/rcol[end]).*B2mE2
         pmodel(x, p) = ( p[1] + p[2] .* x + p[3] .* x.^2 + p[4] .* x.^3 + p[5] .* x.^4 + p[6] .* x.^5 )
         pfit   = curve_fit(pmodel, rcol, ∂μUnew, [0., 0., 0., 0., 0., 0.])
         ∂μU[1:idx_r2] = pmodel(rcol, pfit.param)

### 2018-06-23 scripts/func.jl

@@ -237,8 +237,8 @@ function Fsq(U::Array{Float64, 2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I)
     fsq_exp   = 0. #0.1*exp(-(r-crd.rmin)/0.1)
     B2mE2_exp = B2pE2.*fsq_exp
 
-    fsq2_spl = Spline1D(Ucol, (fsq-fsq_exp).^2)
-    fsq2_avg = integrate(fsq2_spl, Ucol[1], Ucol[end])/(Ucol[end]-Ucol[1])
+    fsq2_spl = Spline1D(Ucol[2:end], (fsq[2:end]-fsq_exp).^2)
+    fsq2_avg = integrate(fsq2_spl, Ucol[2], Ucol[end])/(Ucol[end]-Ucol[2])
 
     # plot(Ucol, Icol.^2, "k")
     # plot(Ucol, κcol .* (Δ .* ∂rU.^2 + ∂μU.^2)./Σ, "r")
@@ -247,4 +247,27 @@ function Fsq(U::Array{Float64, 2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I)
     plot(Ucol, B2mE2)
     plot(Ucol, B2mE2_exp, "--")
     return Ucol, B2mE2, B2mE2_exp, fsq, fsq2_avg
+end
+
+function Fsq_only(U::Array{Float64, 2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I)
+    idx = crd.idx_r2
+    ∂1U = zeros(idx);  ∂1U[2:idx] = (U[1, 2:idx] - U[1, 1:idx-1]) ./ crd.δR
+    ∂2U = (U[2, 1:idx] - U[1, 1:idx]) ./ crd.δμ
+
+    Rcol = crd.R[1, 1:idx]
+    ∂rU  = ∂1U .* (1-Rcol).^2; ∂μU = ∂2U
+
+    μ = 0.
+    r = crd.rcol[1:idx]
+    Δ = r.^2 - 2r + crd.a^2
+    Σ = r.^2 + crd.a^2 * μ.^2
+    β = Δ .* Σ + 2r .*(r.^2+crd.a^2)
+
+    Ωspl = Ω_I.Ωspl
+    Ucol = U[1,1:idx]
+    Icol = 2*Ωspl(Ucol).*Ucol
+    κcol = grd.κ[1,1:idx]
+
[…]

### 2018-06-23 scripts/run.jl

@@ -4,7 +4,7 @@ include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 4.0)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 4.5)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
@@ -12,11 +12,11 @@ grd      = Grid(crd, mtr, Ω_I)
 ils      = LS(U, grd, crd, Ω_I)
 lsn      = LS_neighbors(U, ils, grd, crd)
 bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 0)  # 0:init, else:updater
+Ωpar_loop= 1
 
-δU        = zeros(crd.μlen); Res = 0.
-Ωpar_loop = 1; fsq2_avg  = 0.1
+δU = zeros(crd.μlen); Res = 0.; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 5) & (fsq2_avg > 1.e-4)
+while (Ωpar_loop <= 20) & (fsq2_avg > 1.e-4)
     for BCloop = 1:15
         for Ωloop = 1:150
             for Iloop = 1:5
@@ -31,7 +31,7 @@ while (Ωpar_loop <= 5) & (fsq2_avg > 1.e-4)
             ils, Ω_I = LS_updater!(U, grd, crd, Ω_I, ils, Ω_par)     #update ils and Ω_I.Ωspl from (ils.ULS, ils.Ω)
             lsn      = LS_neighbors(U, ils, grd, crd)
         end
-            bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 1, Isf = 6.0)
+            bc_eqt   = BC_gen(U, crd, grd, Ω_I, BC_opt = 1, Isf = 6.0)
             Ubm = linspace(0., U_H, 64)
             plot(Ubm, Ω_I.Ωspl(Ubm))
             plot(Ubm, Ω_I.Ispl(Ubm)/U_H)
@@ -45,7 +45,7 @@ while (Ωpar_loop <= 5) & (fsq2_avg > 1.e-4)
[…]

### 2018-06-24 plot.jl
state save

@@ -1,27 +1,0 @@
-using PyPlot
-using JLD
-include("scripts/GS.jl")
-include("scripts/SOR.jl")
-include("scripts/func.jl")
-
-Ω_sim = readdlm("/home/zhenpan/Astroph/Uniform_Sol/psi_omegaf_a_0.990.out")
-@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a99_Icrt.jld"
-
-Ubm = linspace(0., U_H, 64)
-fig = figure(figsize=(5, 3.6))
-plot(Ubm/U_H, Ω_I.Ωspl(Ubm)/crd.Ω_H, lw = 2, "k")
-plot(Ubm/U_H, 0.5*(1-Ubm/U_H), lw = 2, "r--")
-plot(Ω_sim[:,1]/Ω_sim[end,1], Ω_sim[:,2], lw = 2)
-ylim(0., 0.52)
-xlabel(L"$A_\phi$", fontsize = 20)
-ylabel(L"$\Omega/ \Omega_{\rm H}$", fontsize = 20)
-tick_params(axis="both", which="major", length =4, labelsize=14)
-ax = gca()
-mx = matplotlib[:ticker][:MultipleLocator](0.2)
-My = matplotlib[:ticker][:MultipleLocator](0.1) # Define interval of major ticks
-my = matplotlib[:ticker][:MultipleLocator](0.05)
-ax[:xaxis][:set_minor_locator](mx)
-ax[:yaxis][:set_major_locator](My)
-ax[:yaxis][:set_minor_locator](my)
-tight_layout()
-savefig("f2b.pdf")

### 2018-06-24 scripts/SOR.jl

@@ -86,14 +86,15 @@ function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_op
         iip  = Ispl(Ucol).*derivative(Ispl, Ucol)
         IIp  = Ω_I.IIpspl(Ucol)
 
-        #∂μU_zj = Ispl(Ucol[1])*crd.rmin/2./(Ω_I.Ωspl(Ucol[1])-crd.Ω_H)
+        #Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
 
-        Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
-
-        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip) - 0.04*(1.-rcol/rcol[end]).*B2mE2
+        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip)   #- 0.04*(1.-rcol/rcol[end]).*B2mE2
         pmodel(x, p) = ( p[1] + p[2] .* x + p[3] .* x.^2 + p[4] .* x.^3 + p[5] .* x.^4 + p[6] .* x.^5 )
         pfit   = curve_fit(pmodel, rcol, ∂μUnew, [0., 0., 0., 0., 0., 0.])
         ∂μU[1:idx_r2] = pmodel(rcol, pfit.param)
+
+        (xmax, idx_max) = findmax(∂μU[1:idx_r2])
+        ∂μU[1:idx_max]  = xmax 
     end
 
     ∂μU[idx_r2+1:idx_bd] = ∂μU[idx_r2]*exp(-(crd.rcol[idx_r2+1:idx_bd]-2.).^2/(2*0.05^2))

### 2018-06-24 scripts/func.jl

@@ -119,10 +119,8 @@ function Ωpar_updater!(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_
     Ucol = reverse(ils.ULS); U_H =  Ucol[end]
 
     Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
-    Icrt2_spl  = Spline1D(Ueqt, B2mE2-B2mE2_exp, bc="zero")
-    I_eqt = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt2_spl(Ucol)
-    #Icrt1 = Ω_I.Ispl(Ucol) - 2*Ω_I.Ωspl(Ucol).*Ucol
-    #I_hrz = 2*Ω_I.Ωspl(Ucol).*Ucol + Isf*Icrt
+    Icrt_spl  = Spline1D(Ueqt[2:end], B2mE2[2:end], bc="zero")
+    I_eqt = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt_spl(Ucol)
     I_hrz = Ω_I.Ispl(Ucol)
     I_new = I_hrz.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1]) + I_eqt.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1])
 

### 2018-06-24 scripts/run.jl

@@ -4,19 +4,76 @@ include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 4.5)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.95, rmax = 100., xbd = 4.5)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
 grd      = Grid(crd, mtr, Ω_I)
 ils      = LS(U, grd, crd, Ω_I)
 lsn      = LS_neighbors(U, ils, grd, crd)
-bc_eqt   = BC_gen(U, crd, Ω_I, BC_opt = 0)  # 0:init, else:updater
+bc_eqt   = BC_gen(U, crd, grd, Ω_I, BC_opt = 0)  # 0:init, else:updater
 Ωpar_loop= 1
 
 δU = zeros(crd.μlen); Res = 0.; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 20) & (fsq2_avg > 1.e-4)
+while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
+    for BCloop = 1:15
+        for Ωloop = 1:150
+            for Iloop = 1:5
+                U,  Res, dU = Solver!(U, crd, grd, Ω_I, ils, lsn, maxitr = 2, omega = 1.0)
+                U, U_H      = Bounds!(U, crd, Ω_I, lsn, bc_eqt)                  #where bc_eqt contains ∂μU on equator
+                ils,Ω_I, δU = IIp_updater!(U, crd, Ω_I, ils, lsn, Isf = 0.08)    #update IIp in ils and Ω_I
+                grd         = Grid!(grd, crd, mtr, Ω_I)                          #update IIp in grd
+            end
+            println("(Ωpar-BC-Ωloop) = ($Ωpar_loop $BCloop $Ωloop), Res = $(sum(abs(Res))), U_H = $U_H, U_he = $(U[1,1])")
+            Ω_I      = ΩI_updater!(U, crd, Ω_I, ils, Ω_par)
+            grd      = Grid(crd, mtr, Ω_I)
[…]

### 2018-06-25 scripts/SOR.jl
paper writing

@@ -66,14 +66,14 @@ function Bounds!(U::Array{Float64,2}, crd::Cord, Ω_I::Ω_and_I, lsn::LS_neighbo
     return U, U_H
 end
 
-function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_opt = 0, Isf = 5.)
+function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_opt = 0, Isf = 5., Isf_BE = 0.)
     idx_r2  = crd.idx_r2
     idx_bd  = crd.idx_xbd[1]
     rmin    = crd.rmin
     ∂μU     = zeros(idx_bd)
 
     if BC_opt==0
-        ∂μU[1:idx_r2] = -1.*(crd.rcol[1:idx_r2]/rmin).^2.8
+        ∂μU[1:idx_r2] = -1.5*(crd.rcol[1:idx_r2]/rmin).^2.8 #-1.*(crd.rcol[1:idx_r2]/rmin).^2.8
     else
         ∂μU[1:idx_r2] = (U[2,1:idx_r2]-U[1,1:idx_r2])/crd.δμ
 
@@ -86,15 +86,15 @@ function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_op
         iip  = Ispl(Ucol).*derivative(Ispl, Ucol)
         IIp  = Ω_I.IIpspl(Ucol)
 
-        #Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
+        Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
 
-        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip)   #- 0.04*(1.-rcol/rcol[end]).*B2mE2
+        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip) - Isf_BE*(1.-rcol/rcol[end]).*B2mE2
         pmodel(x, p) = ( p[1] + p[2] .* x + p[3] .* x.^2 + p[4] .* x.^3 + p[5] .* x.^4 + p[6] .* x.^5 )
         pfit   = curve_fit(pmodel, rcol, ∂μUnew, [0., 0., 0., 0., 0., 0.])
[…]

### 2018-06-25 scripts/func.jl

@@ -27,13 +27,15 @@ end
 function USmooth!(U::Array{Float64,2}, lsn::LS_neighbors, crd::Cord)
     for μidx = 2:crd.μlen-1
         Ridx = lsn.lsn_idx[μidx]
-        x    = [crd.R[μidx, Ridx-2], crd.R[μidx, Ridx+3]]
-        y    = [U[μidx, Ridx-2], U[μidx, Ridx+3]]        #the next near points
-        spl  = Spline1D(x, y, k=1)
-        U[μidx, Ridx-1] = spl(crd.R[μidx, Ridx-1])
-        U[μidx, Ridx]   = spl(crd.R[μidx, Ridx])
-        U[μidx, Ridx+1] = spl(crd.R[μidx, Ridx+1])
-        U[μidx, Ridx+2] = spl(crd.R[μidx, Ridx+2])
+        if Ridx > 2
+            x    = [crd.R[μidx, Ridx-2], crd.R[μidx, Ridx+3]]
+            y    = [U[μidx, Ridx-2], U[μidx, Ridx+3]]        #the next near points
+            spl  = Spline1D(x, y, k=1)
+            U[μidx, Ridx-1] = spl(crd.R[μidx, Ridx-1])
+            U[μidx, Ridx]   = spl(crd.R[μidx, Ridx])
+            U[μidx, Ridx+1] = spl(crd.R[μidx, Ridx+1])
+            U[μidx, Ridx+2] = spl(crd.R[μidx, Ridx+2])
+        end
     end
 
     for μidx = 2:crd.μlen-1

### 2018-06-25 scripts/run.jl

@@ -4,7 +4,7 @@ include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-crd      = Cord(Rlen = 512, μlen = 64, a = 0.95, rmax = 100., xbd = 4.5)
+crd      = Cord(Rlen = 512, μlen = 64, a = 0.99, rmax = 100., xbd = 4.5)
 mtr      = Geom(crd)
 Ω_par    = [0.1, 0.02, 0.04, 0.0]
 U, Ω_I, U_H   = Init(crd, mtr, Ω_par)
@@ -16,7 +16,7 @@ bc_eqt   = BC_gen(U, crd, grd, Ω_I, BC_opt = 0)  # 0:init, else:updater
 
 δU = zeros(crd.μlen); Res = 0.; fsq2_avg  = 0.1
 
-while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
+while (Ωpar_loop <= 15) & (fsq2_avg > 2.e-4)
     for BCloop = 1:15
         for Ωloop = 1:150
             for Iloop = 1:5
@@ -42,7 +42,7 @@ while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
             plot(Ubm, Ispl(Ubm)/U_H, "k--")
             plot(Ubm, Ispl(Ubm).*derivative(Ispl, collect(Ubm))/U_H, "k--")
     end
-    Ω_par, fsq2_avg =  Ωpar_updater!(U, crd, grd, Ω_I, ils, Isf = 0.02)
+    Ω_par, fsq2_avg =  Ωpar_updater!(U, crd, grd, Ω_I, ils, Isf = 0.06)
     Ωpar_loop +=1
     println("fsq2_avg = $fsq2_avg")
     @save "/home/zhenpan/Astroph/Uniform_Sol/scripts/a$(crd.a).jld" Ωpar_loop crd mtr Ω_par U Ω_I U_H grd ils lsn δU bc_eqt fsq2_avg
@@ -69,11 +69,11 @@ include("scripts/GS.jl")
 include("scripts/SOR.jl")
 include("scripts/func.jl")
 
-@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a998.jld"
+@load "/home/zhenpan/Astroph/Uniform_Sol/scripts/a0.99.jld"
 
-δU = zeros(crd.μlen); Res = 0.; fsq2_avg  = 0.1
[…]

### 2018-06-25 paper/ms.tex
paper writing
state save

@@
 \label{eq:nbc}
-\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Big/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
+\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Bigg/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
 \ee
 as a proxy of the marginally force-free equatorial boundary condition (\ref{eq:bc3}),
-where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.
+where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively;
+and we choose $B^2+E^2$ to be the energy density measured by the zero-angular-momentum-observers.
 Specifically,
@@
 \ee
-where $B^2+E^2$ is the energy density measured by the zero-angular-momentum-observers.
 
@@
 \begin{align}
-    \Ap &= r^2 \sst,  \label{eq:gss1} \\
+    \Ap &= \frac{B_0}{2}r^2 \sst,  \label{eq:gss1} \\
     \Omega & = 0.5\WH\left(1-\Ap/\AHE\right),  \label{eq:gss2}\\
@@
 
-2. We evolve the GS equation (\ref{eq:GSg}) and adjust $II'(\Ap)$ enabling smooth field lines across the LS
-\cite[see e.g.][for details]{Contopoulos2013, Nathanail2014, Pan2016a, Mahlmann2018}.
+2. We evolve the GS equation (\ref{eq:GSg}) using the well-known relaxation method \cite{Press1987}
+ and adjust $II'(\Ap)$ until  field lines smoothly cross the LS
+\cite[see e.g.][for more details]{Contopoulos2013, Nathanail2014, Pan2016a, Mahlmann2018}.
 
 3. Usually the current $I$ found in Step 2 neither satisfies the radiation condition (\ref{eq:rad})
-nor guarantees the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
+nor guarantees the boundary condition (\ref{eq:bc3}). We  adjust
 $\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
@@
 \ee
-enabling the radiation condition (\ref{eq:rad}) for
-$A_\phi\in [A_\phi^{\rm HE}, A_\phi^{\rm EE}]$, where $\zeta_1$ is an
-empirical step size.
+where $\zeta_1$ is an
+empirical step size. For each new $A_{\phi,\mu}$, we repeat Step 2
+until $\Am(\mu = 0, r_+ \leq r\leq 2)$ converges, i.e. the condition $2\Omega\Ap(2\Omega\Ap)' = II'$ is
+achieved for $A_\phi\in (A_\phi^{\rm HE}, A_\phi^{\rm EE})$.
 
@@
  \be
-\Omega_{\rm new} = \frac{I}{2\Ap}\Bigg|_{0 < \Ap < \AHE},
+2\Ap\Omega_{\rm new}  = I|_{0 < \Ap < \AHE},
  \ee
- and the second part can be realized by
+ and the second part can be realized by iterative correction
  \be
-\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Bigg|_{\mu=0, r_+\leq r \leq 2},
+2\Ap(\Omega_{\rm new} - \Omega_{\rm old}) =  - \zeta_2\times\Delta (B^2-E^2)|_{\mu=0, r_+\leq r \leq 2},
  \ee
@@
  velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ on the whole range
- $[0, \AEE]$ via a fifth-order polynomial.
+ $(0, \AEE)$ via a fifth-order polynomial.
 
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-which displays three generic features: (1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
+and in the upper panel of Figure \ref{fig:omega}, we show the angular velocity functions $\Omega(A_\phi)$ for different BH spins.
+Combining the two figures, we see three generic features: (1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
 (2) there is no current sheet within the magnetosphere except the equatorial current sheet extending from $r_+$ to $2M$,
-which gives rise to a cusp to the magnetic field lines,
+which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines,
 (3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
 both of which carry electric current and therefore Poynting flux.
+
+In the lower panel of Figure  \ref{fig:omega} and in Figure \ref{fig:Edot}, we compare our numerical results with
+recent high-resolution simulations performed by East and Yang \cite{East2018} (EY Sims). In Figure \ref{fig:Edot}, the solid
+lines are curves fitted by polynomials
+
+We find the angular velocity functions
+in two studies show a good agreement, while the value of our magnetic flux $\AEE$ is lower by $\sim 5\%$, which gives
+to $\sim 10\%$ lower energy extraction rates.
 
@@
 \begin{figure}
-\includegraphics[scale=0.6]{f2}
-\caption{\label{fig:omega} Solid: the angular velocity function $\Omega(\Ap)$ for $a=0.99$.
-Dashed: a linear function for comparison.}
+\includegraphics[scale=0.6]{f2a}
+\includegraphics[scale=0.6]{f2b}
+\caption{\label{fig:omega} Upper panel: the angular velocity functions $\Omega(\Ap)$ for different BH spins.
+Lower Panel: comparison of our numerical results (solid lines) with the simulation results in \cite{East2018} (dashed lines).}
 \end{figure}
 
-\section{Comparison with previous studies}
+\begin{figure}
+\includegraphics[scale=0.6]{f3}
+\caption{\label{fig:Edot} Comparison of the energy extraction rate $\dot E(\WH)$ derived from our
+numerical solutions and from the simulations \cite{East2018},
+where the former is lower than the latter one by $~10\%$.}
+\end{figure}
+
+\section{Discussions}
 
@@
 
-\section{Summary and Discussions}
+\section{Summary}
 

### 2018-06-26 paper/ms.tex
state save

@@
 \author{Zhen Pan}
-\email{zhpan@ucdavis.edu}
+\email{zpan@perimeterinstitute.ca}
 \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario N2L 2Y5, Canada}
@@
 \section{Introduction}
+
+The paper is organized as follows.  In Section \ref{sec:basic}, we outline the basic governing equations.
+In Section \ref{sec:uni_sol}, we clarify the radiation condition, boundary conditions and numerical algorithm
+for the uniform field solution. In Section \ref{sec:discussion}, we discuss the solution uniqueness, near-horizon
+field line configuration and the application to general field line configurations. Summary is given in Section \ref{sec:summary}.
 
@@
 \section{Uniform field solution}
+\label{sec:uni_sol}
+
+\subsection{Solution uniqueness and radiation condition}
+For common field configurations, including split monopole and parabola, there exist two LSs where
+the LS function vanishes and the GS equation degrades from second order to first order. As proposed
+by Contopoulos et.al. \cite{Contopoulos2013}, one can adjust the two free functions $\Omega(\Ap)$
+and $I(\Ap)$ enabling field lines smoothly cross the two LSs, then the solution
+$\{\Omega(\Ap), I(\Ap), \Ap(r,\theta)\}$  is uniquely found. But for the vertical field lines, their
+exist only one LS, which is insufficient to determine two free functions. Therefore people have been
+wondering the possibility of many solutions though the many-solutions scenario is not supported by force-free
+dynamics simulations. To tackle this problem, we proposed that the two functions are not independent;
+instead, they are related by the radiation condition \cite{Pan2016a, Pan2017}
+\be I = 2\Omega A_\phi, \label{eq:rad}\ee
+which has been confirmed by the recent high-accuracy simulations \cite{East2018}.
 
@@
 
-The boundary conditions
+The boundary conditions at infinity (inner infinity $r=r_+$ and outer infinity $r\rightarrow\infty$)
+and on the polar axis can be simply set as
+\be
+\begin{aligned}
+\Ar|_{r=r_+, \infty} &= 0, \\
+A_\phi|_{\mu = 1} &= 0,\\
+\end{aligned}
+\ee
+where $r_+$ is the radius of the event horizon,
+while the equatorial boundary conditions are more unclear until recent simulations \cite{East2018}
+come out which show that there exists an equator current sheet within the ergosphere where the
+magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$. Motivated by these simulations,
+we choose the following equatorial boundary condition in our numerical solutions,
 \begin{subequations}
 \begin{align}
-    A_\phi(\mu = 1) &= 0,  \label{eq:bc1}\\
     \Am(\mu = 0, r > 2) &= 0, \label{eq:bc2}\\
@@
 \end{subequations}
-where $r_+$ is the radius of the event horizon.
+In fact, Equation (\ref{eq:bc3})
+is neither a Dirichlet nor a Neumann boundary condition, since
+\be
+\begin{aligned}
+&B^2-E^2 \\
+= & \frac{1}{\Sigma \sst} \left[ -\mathcal{K} \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right],
+\end{aligned}
+\ee
+which involves both derivatives $\Am$ and $\Ar$ on the boundary.
+Therefore, it is numerically non-trivial to impose this boundary condition in computation.
 
-In our computation, we use following numerical prescription
+In addition, there is a coordinate singularity $1/\Delta$ in the expression of $B^2-E^2$.
+To avoid possible numerical difficulty, we use following prescription
 \be
 \label{eq:nbc}
-\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \frac{B^2-E^2}{B^2+E^2} dA_\phi \Bigg/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
+\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \left(\frac{B^2-E^2}{B^2+E^2}\right)^2 dA_\phi \Bigg/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
 \ee
-as a proxy of the marginally force-free equatorial boundary condition (\ref{eq:bc3}),
-where ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively;
-and we choose $B^2+E^2$ to be the energy density measured by the zero-angular-momentum-observers.
-Specifically,
+in our computation, as a proxy of the marginally force-free equatorial boundary condition (\ref{eq:bc3}),
+where $\AHE$ and $\AEE$ are the magnetic flux entering the horizon and the ergosphere, respectively;
+``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.
+For definiteness, we choose $B^2+E^2$ to be the energy density measured by the zero-angular-momentum-observers.
+Explicitly, we have
 \be
 \begin{aligned}
-B^2-E^2 &= \frac{1}{\Sigma \sst} \left[ -\mathcal{K} \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right]\\
-B^2+E^2 &= \frac{1}{\Sigma \sst} \left[ \left(\mathcal{K}+\frac{\Delta\Sigma}{\beta} \right) \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right]\\
+ & B^2+E^2   \\
+=& \frac{1}{\Sigma \sst} \left[ \left(\mathcal{K}+\frac{\Delta\Sigma}{\beta} \right)
+ \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)
+ +\frac{\Sigma}{\Delta}I^2\right]
 \end{aligned}
@@
 
+\subsection{Generic features of the BH magnetosphere structure}
+Before delving into the details of numerically solving the GS equations,
+we point out that from the radiation condition (\ref{eq:rad}) and the marginally
+force-free boundary condition (\ref{eq:bc3})
+themselves contains rich information about the BH magnetosphere structure.
+
+Let's first find out where the LS intersect with the equator, $r_{\rm LS}|_{\mu=0}$.
+From the expression of the LS function, it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
+At this point,  the LS function $\mathcal K$ vanishes,
+and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
+which in turns indicates a vanishing angular velocity $\Omega$ from
+the radiation condition (\ref{eq:rad}).  Due to the static limit, $\Omega$
+must be non-zero inside the ergosphere.  Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$, i.e.
+to satisfy the boundary condition (\ref{eq:bc3}), the LS must interact the equator at $r=2$, which also
+justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) .
+
+From above analysis, we expect several generic features in the magnetospheres that are independent
+of the GS equation:
+(1) the LS runs from $r=r_+$ to $r=2$ as $\theta$ varies from $0$ to $\pi/2$,
+(2) there is no current sheet within the magnetosphere except the equatorial current
+sheet extending from $r_+$ to $2$, which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines,
+(3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
+both of which carry electric current and therefore Poynting flux. With the guidance of the qualitative
+features above, we are to numerically solve the GS equation and quantify these features.
+
 \subsection{Numerical method}
-We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ connected by the radiation condition
-\be I = 2\Omega A_\phi, \label{eq:rad}\ee
+We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition (\ref{eq:rad})
 and enabling field lines smoothly crossing the LS,
 and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
-guaranteeing the boundary condition (\ref{eq:bc3}).
+guaranteeing the boundary condition (\ref{eq:bc3}), which itself cannot be directly
+used in computation.
 
@@
 computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
-and implement a uniform $512\times 64$ grid. The detailed algorithm is clarified
+and implement a uniform $512\times 64$ grid. The numerical algorithm for
+searching desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$ is detailed
 in the following steps.
@@
  \ee
- and the second part can be realized by iterative correction
+ and the second part can be realized by iterative corrections
  \be
@@
 and in the upper panel of Figure \ref{fig:omega}, we show the angular velocity functions $\Omega(A_\phi)$ for different BH spins.
-Combining the two figures, we see three generic features: (1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
-(2) there is no current sheet within the magnetosphere except the equatorial current sheet extending from $r_+$ to $2M$,
-which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines,
-(3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
-both of which carry electric current and therefore Poynting flux.
-
-In the lower panel of Figure  \ref{fig:omega} and in Figure \ref{fig:Edot}, we compare our numerical results with
-recent high-resolution simulations performed by East and Yang \cite{East2018} (EY Sims). In Figure \ref{fig:Edot}, the solid
-lines are curves fitted by polynomials
-
-We find the angular velocity functions
-in two studies show a good agreement, while the value of our magnetic flux $\AEE$ is lower by $\sim 5\%$, which gives
-to $\sim 10\%$ lower energy extraction rates.
 
@@
 \includegraphics[scale=0.6]{f3}
-\caption{\label{fig:Edot} Comparison of the energy extraction rate $\dot E(\WH)$ derived from our
-numerical solutions and from the simulations \cite{East2018},
-where the former is lower than the latter one by $~10\%$.}
+\caption{\label{fig:Edot} Comparison of the energy extraction rate $\dot E(\WH)$ obtained from our
+numerical solutions and from the high-resolution force-free simulations \cite{East2018},
+where the former is lower than the latter by $\sim 10\%$ for large spins.}
 \end{figure}
 
+With the angular velocity $\Omega(\Ap)$ available, the energy extraction rate from the BH is known as
+\be
+\label{eq:Edot}
+\dot E = 4\pi \int_0^{\AEE} \Omega \times I \ d \Ap.
+\ee
+In the limit of slow rotation, analytic solution is known as \cite{Pan2014, East2018},
+\be
+    \Omega = \WH\frac{\sqrt{1-\psi}} {1+\sqrt{1-\psi}},
+\ee
+where $\psi = \Ap/(2B_0M^2)$, and the energy extraction rate is
+\be
+\label{eq:lowEdot}
+\dot E = 128\pi \left(\frac{17}{24}-\ln 2\right) B_0^2 M^4 \WH^2.
+\ee
+
+In the lower panel of Figure  \ref{fig:omega} and in Figure \ref{fig:Edot}, we compare our numerical results with
+recent high-resolution simulations done by East and Yang \cite{East2018}. In Figure \ref{fig:Edot},
+the points are taken from either the simulations or our numerical solutions, while the solid lines are
+corresponding polynomial fitting curves which require to approach Eq.(\ref{eq:lowEdot}) for small spins and to be flat for extremal spins.
+We find the angular velocity functions obtained from two different approaches yield a good agreement (Figure \ref{fig:omega}),
+while the energy extraction rate $\dot E$ is $\sim 10\%$ lower than the corresponding simulation results, which is traced to
+$\sim 5\%$ smaller magnetic flux $\AEE$ in our numerical solutions.
+
 \section{Discussions}
+\label{sec:discussion}
 
-\subsection{Solution uniqueness}
+\subsection{General application}
+In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
+being strictly vertical. Due to the same topology, it is reasonable to expect the marginally force-free boundary
+condition (\ref{eq:bc3}) is also a good work approximation. The features we observed the uniform field solution
+should also apply here. The numerical method for solving the GS equation and self-consistently imposing the boundary
+condition (\ref{eq:bc3}).
 
-\subsection{Topology of near-horizon field lines}
+\subsection{Near-horizon field lines}
+In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
+around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event
+horizon" based on two
+However, simulations shows that there exists an equatorial current sheet within the ergosphere, where
+the force-free condition breaks down.
 
 \section{Summary}
+\label{sec:summary}
+
+In this paper, we revisit the problem of the uniform field solution to the BZ mechanism.
 

### 2018-06-26 paper/ms.tex
save

@@
 In addition, there is a coordinate singularity $1/\Delta$ in the expression of $B^2-E^2$.
-To avoid possible numerical difficulty, we use following prescription
+To avoid possible numerical difficulty, we use the prescription
 \be
 \label{eq:nbc}
-\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \left(\frac{B^2-E^2}{B^2+E^2}\right)^2 dA_\phi \Bigg/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3}.
+\int_{A_\phi^{\rm HE}}^{A_\phi^{\rm EE}} \left(\frac{B^2-E^2}{B^2+E^2}\right)^2 dA_\phi \Bigg/ \left(A_\phi^{\rm EE}- A_\phi^{\rm HE}\right)  < 10^{-3},
 \ee
@@
 \subsection{Generic features of the BH magnetosphere structure}
+\label{subsec:features}
 Before delving into the details of numerically solving the GS equations,
-we point out that from the radiation condition (\ref{eq:rad}) and the marginally
+here we point out that from the radiation condition (\ref{eq:rad}) and the marginally
 force-free boundary condition (\ref{eq:bc3})
-themselves contains rich information about the BH magnetosphere structure.
+themselves contain rich information about the BH magnetosphere structure.
 
@@
 From the expression of the LS function, it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
-At this point,  the LS function $\mathcal K$ vanishes,
+On this point,  the LS function $\mathcal K$ vanishes,
 and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
@@
 (1) the LS runs from $r=r_+$ to $r=2$ as $\theta$ varies from $0$ to $\pi/2$,
-(2) there is no current sheet within the magnetosphere except the equatorial current
+(2) since $I$ vanishes at $r_{\rm LS}|_{\mu=0}$, we expect no current sheet within the magnetosphere except the equatorial current
 sheet extending from $r_+$ to $2$, which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines,
 (3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
-both of which carry electric current and therefore Poynting flux. With the guidance of the qualitative
-features above, we are to numerically solve the GS equation and quantify these features.
+both of which carry electric current and therefore Poynting flux.
+
+With the guidance of the qualitative features above, we are to numerically
+solve the GS equation and quantify these features.
 
@@
 and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
-guaranteeing the boundary condition (\ref{eq:bc3}), which itself cannot be directly
-used in computation.
+guaranteeing the boundary condition (\ref{eq:bc3}).
 
@@
 \be
+\label{eq:bc_crt}
  A_{\phi,\mu}|_{\rm new}  = A_{\phi,\mu}|_{\rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
 \ee
-where $\zeta_1$ is an
-empirical step size. For each new $A_{\phi,\mu}$, we repeat Step 2
-until $\Am(\mu = 0, r_+ \leq r\leq 2)$ converges, i.e. the condition $2\Omega\Ap(2\Omega\Ap)' = II'$ is
+where $\zeta_1$ is an empirical step size. For each new $A_{\phi,\mu}$, we repeat Step 2 and iterative
+correction (\ref{eq:bc_crt}) until $\Am(\mu = 0, r_+ \leq r\leq 2)$ converges, i.e. the condition $2\Omega\Ap(2\Omega\Ap)' = II'$ is
 achieved for $A_\phi\in (A_\phi^{\rm HE}, A_\phi^{\rm EE})$.
@@
  for $A_\phi \in (0, A_\phi^{\rm HE})$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
- enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in [\AHE, \AEE]$.
+ enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in (\AHE, \AEE)$.
  The first part is straightforward, i.e.,
@@
  \ee
- and the second part can be realized by iterative corrections
+ and the second part can be realized by iterative correction
  \be
@@
  5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat Step 2 to Step 4,
- until the numerical prescription (\ref{eq:nbc}) for the boundary condition (\ref{eq:bc3}) is satisfied.
+ until both the radiation condition (\ref{eq:rad}) and the numerical prescription (\ref{eq:nbc}) for the boundary condition (\ref{eq:bc3}) is satisfied.
 
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-and in the upper panel of Figure \ref{fig:omega}, we show the angular velocity functions $\Omega(A_\phi)$ for different BH spins.
+which explicitly displays the features we anticipated in Section \ref{subsec:features}.
+
+In Figure \ref{fig:omega}, we show the angular velocity function $\Omega(A_\phi)$ for different BH spins and
+compare it with the counterpart obtained from recent high-resolution simulations done by East and Yang \cite{East2018}.
+For reference, we also plot the leading-order analytic solution in the slow-rotation limit \cite{Pan2014, East2018},
+\be
+    \Omega = \WH\frac{\sqrt{1-\psi}} {1+\sqrt{1-\psi}},
+\ee
+where $\psi = \Ap/(2B_0M^2)$.
+From our solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
+$2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
+which is about $\sim 5\%$ lower than the simulation result, while the angular velocity $\Omega$ as a function
+of normalized magnetic flux $\Ap/\AEE$ shows a good agreement with the simulation results.
 
@@
 
-With the angular velocity $\Omega(\Ap)$ available, the energy extraction rate from the BH is known as
+With the angular velocity $\Omega(\Ap)$ obtained, the energy extraction rate from the BH is given by
 \be
@@
 \ee
-In the limit of slow rotation, analytic solution is known as \cite{Pan2014, East2018},
-\be
-    \Omega = \WH\frac{\sqrt{1-\psi}} {1+\sqrt{1-\psi}},
-\ee
-where $\psi = \Ap/(2B_0M^2)$, and the energy extraction rate is
+It is straightforward to obtain the energy extraction rate in the slow-rotation limit
 \be
@@
 
-In the lower panel of Figure  \ref{fig:omega} and in Figure \ref{fig:Edot}, we compare our numerical results with
-recent high-resolution simulations done by East and Yang \cite{East2018}. In Figure \ref{fig:Edot},
+In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$ derived from our numerical solutions with
+East and Yang's simulation results \cite{East2018}, where
 the points are taken from either the simulations or our numerical solutions, while the solid lines are
 corresponding polynomial fitting curves which require to approach Eq.(\ref{eq:lowEdot}) for small spins and to be flat for extremal spins.
-We find the angular velocity functions obtained from two different approaches yield a good agreement (Figure \ref{fig:omega}),
-while the energy extraction rate $\dot E$ is $\sim 10\%$ lower than the corresponding simulation results, which is traced to
-$\sim 5\%$ smaller magnetic flux $\AEE$ in our numerical solutions.
+As expected, our energy extraction rate $\dot E$ is $\sim 10\%$ lower than the corresponding simulation results,
+due to the $\sim 5\%$ smaller magnetic flux $\AEE$.
 
@@
 In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
-being strictly vertical. Due to the same topology, it is reasonable to expect the marginally force-free boundary
+being strictly vertical. Due to the same topology, it is reasonable to expect
+the marginally force-free boundary
 condition (\ref{eq:bc3}) is also a good work approximation. The features we observed the uniform field solution

### 2018-06-27 paper/ms.tex
save

@@
 compare it with the counterpart obtained from recent high-resolution simulations done by East and Yang \cite{East2018}.
-For reference, we also plot the leading-order analytic solution in the slow-rotation limit \cite{Pan2014, East2018},
+For reference, we also plot the leading-order analytic solution in the slow-rotation
+limit \cite{Beskin2013, Pan2014, Gralla2015, East2018},
 \be
@@
 where $\psi = \Ap/(2B_0M^2)$.
-From our solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
+From our numerical solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
 $2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
-which is about $\sim 5\%$ lower than the simulation result, while the angular velocity $\Omega$ as a function
+which is about $\approx 5\%$ lower than the simulation result (Figure 3 of \cite{East2018}),
+while the angular velocity $\Omega$ as a function
 of normalized magnetic flux $\Ap/\AEE$ shows a good agreement with the simulation results.
@@
 \includegraphics[scale=0.6]{f2b}
-\caption{\label{fig:omega} Upper panel: the angular velocity functions $\Omega(\Ap)$ for different BH spins.
-Lower Panel: comparison of our numerical results (solid lines) with the simulation results in \cite{East2018} (dashed lines).}
+\caption{\label{fig:omega} Upper panel: the angular velocity  $\Omega(\Ap)$ for different BH spins.
+Lower Panel: comparison of our numerical results (solid lines) with the simulation results of
+Ref. \cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
+dash-dotted lines.}
 \end{figure}
@@
 \includegraphics[scale=0.6]{f3}
-\caption{\label{fig:Edot} Comparison of the energy extraction rate $\dot E(\WH)$ obtained from our
-numerical solutions and from the high-resolution force-free simulations \cite{East2018},
-where the former is lower than the latter by $\sim 10\%$ for large spins.}
+\caption{\label{fig:Edot} Comparison of the energy extraction rates $\dot E(\WH)$ obtained from
+three different approaches: the leading-order analytic solution (\ref{eq:lowEdot}),
+our numerical solutions and  the high-resolution force-free simulations \cite{East2018}.}
 \end{figure}
@@
 
-In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$ derived from our numerical solutions with
-East and Yang's simulation results \cite{East2018}, where
-the points are taken from either the simulations or our numerical solutions, while the solid lines are
-corresponding polynomial fitting curves which require to approach Eq.(\ref{eq:lowEdot}) for small spins and to be flat for extremal spins.
-As expected, our energy extraction rate $\dot E$ is $\sim 10\%$ lower than the corresponding simulation results,
-due to the $\sim 5\%$ smaller magnetic flux $\AEE$.
+In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$
+derived from our numerical solutions with East and Yang's simulation results
+\cite{East2018}, where the data points are taken from either the simulations
+or our numerical solutions, while the solid lines are corresponding polynomial
+fitting curves which we require to approach Eq.(\ref{eq:lowEdot}) for small
+spins and to be flat for extremal spins. As expected, our energy extraction
+rate $\dot E(\WH)$ is $\approx 10\%$ lower than the corresponding simulation results,
+due to the $\approx 5\%$ smaller magnetic flux $\AEE$.
 
@@
 
-\subsection{General application}
+\subsection{Application to general field configurations}
 In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
@@
 
-\subsection{Near-horizon field lines}
+\subsection{Near-horizon field configuration}
 In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
 around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event
-horizon" based on two
-However, simulations shows that there exists an equatorial current sheet within the ergosphere, where
+horizon".
+However, simulations shows that an equatorial current sheet inevitably forms within the ergosphere , where
 the force-free condition breaks down.

### 2018-06-27 paper/ms.tex
save

@@
 
-\subsection{Generic features of the BH magnetosphere structure}
+\subsection{Generic properties of the BH magnetosphere structure}
 \label{subsec:features}
@@
 \subsection{Numerical method}
+\label{subsec:algorithm}
+
 We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition (\ref{eq:rad})
@@
 \begin{figure}
-\includegraphics[scale=0.55]{f1}
+\includegraphics[scale=0.6]{f1}
 \caption{\label{fig:field_lines} The configuration of field lines for the magnetosphere of a Kerr BH with spin $a=0.99$,
@@
 \begin{figure}
-\includegraphics[scale=0.6]{f2a}
-\includegraphics[scale=0.6]{f2b}
+\includegraphics[scale=0.7]{f2a}
+\includegraphics[scale=0.7]{f2b}
 \caption{\label{fig:omega} Upper panel: the angular velocity  $\Omega(\Ap)$ for different BH spins.
@@
 dash-dotted lines.}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6]{f3}
-\caption{\label{fig:Edot} Comparison of the energy extraction rates $\dot E(\WH)$ obtained from
-three different approaches: the leading-order analytic solution (\ref{eq:lowEdot}),
-our numerical solutions and  the high-resolution force-free simulations \cite{East2018}.}
 \end{figure}
@@
 
+\begin{figure}
+\includegraphics[scale=0.7]{f3}
+\caption{\label{fig:Edot} Comparison of the energy extraction rates $\dot E(\WH)$ obtained from
+three different approaches: the leading-order analytic solution (\ref{eq:lowEdot}),
+our numerical solutions and  the high-resolution force-free simulations \cite{East2018}.}
+\end{figure}
+
 In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$
@@
 
-\section{Discussions}
+\section{Discussion}
 \label{sec:discussion}
@@
 \subsection{Application to general field configurations}
-In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
-being strictly vertical. Due to the same topology, it is reasonable to expect
-the marginally force-free boundary
-condition (\ref{eq:bc3}) is also a good work approximation. The features we observed the uniform field solution
-should also apply here. The numerical method for solving the GS equation and self-consistently imposing the boundary
-condition (\ref{eq:bc3}).
+In real astrophysical environment, we expect the field lines are more close to parabolas instead of
+being strictly vertical. In many previous studies of such field
+configurations \cite[e.g.][]{Tchekhovskoy2010,Nathanail2014,Mahlmann2018},
+due to lacking knowledge of the equatorial boundary condition, the
+equator within the ergosphere was intentionally excluded out of the computation domain by manually
+introducing a ``wall" extending from the horizon-equator intersection to infinity. Such
+simplification obviously misses magnetic field lines rooting on the
+equatorial current sheet, which contribute about half of the total BZ flux for extremal spins in
+the case of vertical field lines.
+
+Due to the resemblance of the vertical field configuration and general parabolic field configurations,
+it is natural to expect an equatorial current develops within the ergosphere,
+where the magnetic dominance loses, therefore the marginally force-free boundary
+condition (\ref{eq:bc3}) should also be a good work approximation here.
+It is straightforward to solve the GS equation and self-consistently
+impose the marginally force-free boundary condition following the
+algorithm detailed in Section \ref{subsec:algorithm}.
+
+The analysis of Section \ref{subsec:features}
 
@@
 In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
-around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event
-horizon".
-However, simulations shows that an equatorial current sheet inevitably forms within the ergosphere , where
+around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event horizon".
+However, simulations shows that an equatorial current sheet inevitably develops within the ergosphere , where
 the force-free condition breaks down.

### 2018-06-28 paper/ms.tex
save

@@
 \section{Introduction}
+
+The Blandford-Znajek (BZ) mechanism \cite{Blandford1977} is believed to be
+one of most efficient ways to extract rotation energy from spinning black holes (BHs),
+which operates in BH systems on all mass scales, from the stellar-mass BHs of gamma-ray
+bursts to the supermassive BHs of active galactic nuclei. In the past decade,
+we have studied the BZ mechanism from different approaches and the cross-check among
+these different approaches has facilitate substantial progress in understanding the BZ mechanism.
+: general relativistic
+magnetohydrodynamic (GRMHD) simulations \cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004},
+analytic solutions \cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015}
+and numerical solutions  \cite{Contopoulos2013,Nathanail2014,Mahlmann2018},
+and all these different approaches give quantitative agreement for simple magnetic field configurations,
+e.g.,
+
+Uniform field solution \cite{Komissarov2004e, Komissarov2005, Komissarov2007,Palenzuela2010,Paschalidis2013,
+Yang2015,Carrasco2017}
 

### 2018-06-30 paper/ms.tex
state

--- 2018-06-27 paper/ms.tex
@@
 \section{Introduction}
+
+The Blandford-Znajek (BZ) mechanism \cite{Blandford1977} is believed to be
+one of most efficient ways to extract rotation energy from spinning black holes (BHs),
+which operates in BH systems on all mass scales, from the stellar-mass BHs of gamma-ray
+bursts to the supermassive BHs of active galactic nuclei. In the past decade,
+we have studied the BZ mechanism from different approaches and the cross-check among
+these different approaches has facilitate substantial progress in understanding the underlying
+detailed physics in the BZ mechanism. Taking the simple monopole magnetic field
+configuration as an example, the solutions obtained from different approaches
+are in quantitative agreement,  see e.g.\cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004}
+for general relativistic magnetohydrodynamic simulations,
+\cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015} for analytic solutions
+and \cite{Contopoulos2013,Nathanail2014,Mahlmann2018} for numerical solutions.
+
+But for other magnetic field configurations, there is no such good agreement, e.g.,
+different approaches do even reach a consensus on the solution uniqueness for uniform field configuration.
+Several force-free electrodynamic simulation \cite{Komissarov2004e, Komissarov2005,
+Komissarov2007,Palenzuela2010,Paschalidis2013, Yang2015,Carrasco2017} have been done
+for investigating this problem. Among these simulations, the BH magnetospheres
+all settle down to a steady state with similar field configuration.
+
+Analytic \cite{Yang2015}
+
+GS equation, one LS, two eigen functions  radiation condition \cite{Pan2017}
+
+Recent sims, radiation condition and the equatorial boundary condition
 
@@
 
-The analysis of Section \ref{subsec:features}
+Numerical solutions for the general parabola field configuration are out of scope of this paper.
+The analysis of Section \ref{subsec:features} which is based on the radiation condition
+and the marginally force-free equatorial boundary condition.
 
@@
 
-In this paper, we revisit the problem of the uniform field solution to the BZ mechanism.
+In the force-free limit, the structure of steady and axisymmetric BH magnetosphere is governed by
+the GS equation, which is a second-order differential equation about the magnetic flux $\Ap$, with two
+free functions $\Omega(\Ap)$ and $I(\Ap)$ to be determined by . For the uniform field configuration, there is only one
+LS, which is insufficient for determine both  $\Omega(\Ap)$ and $I(\Ap)$.
+Therefore the solution uniqueness has been a controversial problem.
+Recent high-accuracy force-free simulations done in Ref. \cite{East2018}
+undoubtedly show that the two functions are not independent;
+instead they are related by the radiation condition (\ref{eq:rad}).
+In addition, an equatorial current sheet within the ergosphere was readily confirmed
+in the simulations
+
+In this paper, we revisit the problem of the uniform field solution.
+From the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
+condition (\ref{eq:bc3}), we derive the
 

### 2018-07-03 paper/ms.tex
save

@@
 \begin{document}
-\title{The force-free magnetosphere of a Kerr black hole: the role of boundary conditions}
+\title{The magnetosphere structure of a Kerr black hole:
+marginally force-free equatorial boundary condition}
 \author{Zhen Pan}
@@
 \begin{abstract}
-    The role of boundary conditions in the structure of
+    The role of equatorial boundary condition in the structure of
     a force-free black hole magnetosphere was rarely discussed, since previous studies have been focused on the
-    the field lines entering the horizon which is causally disconnected and on which the boundary
-    condition imposed usually makes no difference to the magnetosphere structure. However,
-    recent high-resolution general relativistic (GR) force-free simulation shows that there are both
-    field lines entering the horizon and field lines ending up on the equatorial current sheet
+    the field lines entering the horizon. However,
+    recent high-accuracy general relativistic (GR) force-free electrodynamics (FFE) simulations \cite{East2018}
+    show that there are both field lines entering the horizon and field lines ending up on
+    the equatorial current sheet
     within the ergosphere for asymptotic uniform field. For the latter, the equatorial boundary
-    condition is well approximated being marginally force-free, i.e., $B^2-E^2=0$, where $B$ and
-    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit this
-    problem by solving the GR Grad-Shafranov equation which governs the structure of
-    the force-free magnetosphere in steady state and self-consistently imposing the marginally force-free equatorial
-    condition. We also discuss the applicability of this boundary condition and the numerical algorithm proposed
+    condition is well approximated being marginally force-free, i.e., $B^2-E^2\approx 0$, where $B$ and
+    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit uniform field
+    solution to the Kerr BH magnetosphere structure and investigate the role of the marginally force-free
+    equatorial boundary condition in the BH magnetosphere structure.  We find the major qualitative properties of the magnetosphere structure are attributed
+    to the marginally force-free condition without invoking the Grad-Shafranov (GS) equation which governs the structure of
+    the force-free magnetosphere in steady state. We propose an algorithm
+    for numerically solving the GR Grad-Shafranov equation and self-consistently imposing the marginally force-free equatorial
+    condition, and we find a good agreement between our numerical solutions and the high-accuracy FFE simulations.
+    We also discuss the applicability of this boundary condition and the numerical algorithm proposed
     in this paper for general magnetic field configurations.
@@
 these different approaches has facilitate substantial progress in understanding the underlying
-detailed physics in the BZ mechanism. Taking the simple monopole magnetic field
+detailed physics. Taking the simple monopole magnetic field
 configuration as an example, the solutions obtained from different approaches
@@
 for general relativistic magnetohydrodynamic simulations,
-\cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015} for analytic solutions
+\cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015, Grignani2018} for analytic solutions
 and \cite{Contopoulos2013,Nathanail2014,Mahlmann2018} for numerical solutions.
@@
 different approaches do even reach a consensus on the solution uniqueness for uniform field configuration.
-Several force-free electrodynamic simulation \cite{Komissarov2004e, Komissarov2005,
-Komissarov2007,Palenzuela2010,Paschalidis2013, Yang2015,Carrasco2017} have been done
-for investigating this problem. Among these simulations, the BH magnetospheres
-all settle down to a steady state with similar field configuration.
+Several force-free electrodynamics (FFE) simulation \cite{Komissarov2004e, Komissarov2005,
+Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017} have been done,
+the BH magnetospheres in these simulations all settle down to a steady state with similar final field configuration,
+which is an indicator for solution uniqueness.
+However, a family of analytic solutions were presented for slowly spinning BHs \cite{Yang2015, Pan2017}.
+But no instability mode was found for these solutions \cite{Yang2015}, therefore the solution stability
+is not likely the explanation for the solution uniqueness.
 
-Analytic \cite{Yang2015}
+From the viewpoint of numerical solutions, the structure of a BH magnetosphere in axisymmetric and
+steady state is governed by the GS equation, which is a second-order differential equation of
+the magnetic flux $\Ap(r,\theta)$, with two eigenfunctions $I(\Ap)$ and $\Omega(\Ap)$ to be self-consistently
+determined by requiring the magnetic field line smoothly cross the light surfaces (LSs).
+But for the uniform field configuration, there is only one LS, which is insufficient for determining
+the two eigenfunctions. Consequently there should exist infinitely many solutions \cite{Nathanail2014}.
 
-GS equation, one LS, two eigen functions  radiation condition \cite{Pan2017}
-
-Recent sims, radiation condition and the equatorial boundary condition
+To explain the discrepancy about the solution uniqueness from different approaches, Pan et.al. \cite{Pan2017}
+proposed that the two eigenfunctions should be connected by the radiation condition at infinity instead of
+being independent, which was confirmed by recent FFE simulations done
+by East and Yang \cite{East2018}. In addition, there are other interesting features in the structure of the BH
+magnetosphere showing up in the simulations, e.g., an equatorial current sheet naturally develops
+with the ergosphere, and the magnetic dominance marginally loses on the current sheet, i.e. $B^2-E^2\approx 0$.
+Motivated by these simulations, we revisit the uniform field solution and investigate the role of the
+marginally force-free equatorial boundary condition in the BH magnetosphere structure.
+We find the qualitative properties of the BH magnetosphere structure are attributed to the marginally
+force-free equatorial boundary condition without invoking the GS equation.
+We also  propose an algorithm for numerically solving the GS equation and
+consistently imposing the the marginally force-free equatorial boundary condition.
+As a result, we find our numerical solutions are in good agreement with the FFE simulations.
 
@@
 In Section \ref{sec:uni_sol}, we clarify the radiation condition, boundary conditions and numerical algorithm
-for the uniform field solution. In Section \ref{sec:discussion}, we discuss the solution uniqueness, near-horizon
-field line configuration and the application to general field line configurations. Summary is given in Section \ref{sec:summary}.
+for the uniform field solution. In Section \ref{sec:discussion}, we discuss the application
+to general field line configurations and near-horizon
+field line configuration. Summary is given in Section \ref{sec:summary}.
 
@@
 the LS function vanishes and the GS equation degrades from second order to first order. As proposed
-by Contopoulos et.al. \cite{Contopoulos2013}, one can adjust the two free functions $\Omega(\Ap)$
+by Contopoulos et.al. \cite{Contopoulos2013}, one can adjust the two eigenfunctions $\Omega(\Ap)$
 and $I(\Ap)$ enabling field lines smoothly cross the two LSs, then the solution
 $\{\Omega(\Ap), I(\Ap), \Ap(r,\theta)\}$  is uniquely found. But for the vertical field lines, their
-exist only one LS, which is insufficient to determine two free functions. Therefore people have been
-wondering the possibility of many solutions though the many-solutions scenario is not supported by force-free
-dynamics simulations. To tackle this problem, we proposed that the two functions are not independent;
-instead, they are related by the radiation condition \cite{Pan2016a, Pan2017}
+exist only one LS, which is insufficient to determine two eigenfunctions.
+Therefore many solutions are expected \cite{Nathanail2014, Mahlmann2018} but the many-solutions scenario is in
+conflict with several previous FFE simulations.
+To tackle this problem,  Pan et. al. \cite{Pan2016a, Pan2017} proposed that the two eigenfunctions are not independent;
+instead, they are related by the radiation condition at infinity
 \be I = 2\Omega A_\phi, \label{eq:rad}\ee
-which has been confirmed by the recent high-accuracy simulations \cite{East2018}.
+which has been readily confirmed by recent high-accuracy FFE simulations \cite{East2018}.
 
@@
 
-In addition, there is a coordinate singularity $1/\Delta$ in the expression of $B^2-E^2$.
+We note a coordinate singularity $1/\Delta$ in the expression of $B^2-E^2$.
 To avoid possible numerical difficulty, we use the prescription
@@
 
-With the guidance of the qualitative features above, we are to numerically
-solve the GS equation and quantify these features.
+With the guidance of the qualitative properties above, we now proceed to numerically
+solve the GS equation and quantify these properties.
 
@@
 
+In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
+computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
+and implement a uniform $512\times 64$ grid.
 We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition (\ref{eq:rad})
@@
 guaranteeing the boundary condition (\ref{eq:bc3}).
-
-In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
-computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
-and implement a uniform $512\times 64$ grid. The numerical algorithm for
+The numerical algorithm for
 searching desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$ is detailed
@@
 In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
-around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event horizon".
-However, simulations shows that an equatorial current sheet inevitably develops within the ergosphere , where
-the force-free condition breaks down.
+around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event horizon",
+based on the radiation condition $I = \Omega \times \mathcal F(\Ap)$ and the assumption of no current sheet within the ergosphere,
+where the function $F(\Ap)$ is of $\mathcal O(\Ap)$ and  is field configuration dependent. The basic logic is:
+$\Omega$ must be nonzero for all field lines entering the ergosphere due to the static limit; as a result, $I$ must be nonzero
+for these field lines. If there is field line crossing the equator, the electric current either flows. Then
+the charge conservation is violated (if there exists no current sheet).
+
+However, simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
+the force-free condition breaks down. Therefore the above claim should be generalized as
+``in the steady axisymmetric force-free magnetosphere
+around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface
+must intersect the event horizon or end up on the equatorial current sheet".
 
@@
 In this paper, we revisit the problem of the uniform field solution.
-From the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
-condition (\ref{eq:bc3}), we derive the
+We find the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
+condition (\ref{eq:bc3}) are rather informative, which dictate the BH magnetosphere structure
+in various aspects, including the shape of the LS, the near-horizon field line configuration and
+source of BZ flux (see Section \ref{subsec:features} for details). We also propose an algorithm
+for numerically solving the GS equation and consistently imposing the marginally force-free
+equatorial boundary condition. As a result, we find a good agreement between our numerical solutions
+with the high-accuracy FFE simulations.
+
+In realistic astrophysical environment, we expect the magnetic field lines are more close to
+parabolas instead of being strictly vertical. Due to the resemblance, we also expect the marginally
+force-free equatorial boundary condition to be a good working approximation. Though we do not
+numerically solve the GS equation for the parabolic configuration in this paper, the qualitative
+properties discussed in Section \ref{subsec:features} also apply here, since they are dictated by
+the radiation condition and the marginally force-free boundary condition, and GS equation only
+serves to quantify these properties.
+
+\acknowledgements
+
+This research was supported by Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported by the Government of Canada
+through the Department of Innovation, Science and Economic Development Canada
+and by the Province of Ontario through the Ministry of Research, Innovation and Science.
 

### 2018-07-03 paper/ms.tex
save

@@
 To explain the discrepancy about the solution uniqueness from different approaches, Pan et.al. \cite{Pan2017}
-proposed that the two eigenfunctions should be connected by the radiation condition at infinity instead of
+proposed that the two eigenfunctions are connected by the radiation condition at infinity instead of
 being independent, which was confirmed by recent FFE simulations done
@@
 
-Let's first find out where the LS intersect with the equator, $r_{\rm LS}|_{\mu=0}$.
+Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
 From the expression of the LS function, it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
@@
 which in turns indicates a vanishing angular velocity $\Omega$ from
-the radiation condition (\ref{eq:rad}).  Due to the static limit, $\Omega$
+the radiation condition (\ref{eq:rad}).  Due to the frame-dragging effect, $\Omega$
 must be non-zero inside the ergosphere.  Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$, i.e.
@@
 guaranteeing the boundary condition (\ref{eq:bc3}).
-The numerical algorithm for
-searching desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$ is detailed
-in the following steps.
+
+The numerical algorithm for searching desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$
+is detailed in the following steps.
 
@@
 $\{ \Omega(\Ap), I(\Ap)\}$
-and equatorial boundary condition as follows
+and equatorial boundary condition of Neumann type as follows
 \begin{subequations}
@@
  and adjust $II'(\Ap)$ until  field lines smoothly cross the LS
-\cite[see e.g.][for more details]{Contopoulos2013, Nathanail2014, Pan2016a, Mahlmann2018}.
+\cite[see e.g.][for more details]{Contopoulos2013, Nathanail2014, Pan2017, Mahlmann2018}.
 
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-which explicitly displays the features we anticipated in Section \ref{subsec:features}.
+which explicitly displays the features we anticipated in Section \ref{subsec:features} and is consistent with
+the simulation results \cite{East2018}.
 
 In Figure \ref{fig:omega}, we show the angular velocity function $\Omega(A_\phi)$ for different BH spins and
-compare it with the counterpart obtained from recent high-resolution simulations done by East and Yang \cite{East2018}.
+compare it with the counterpart obtained from the simulations \cite{East2018}.
 For reference, we also plot the leading-order analytic solution in the slow-rotation
@@
 where $\psi = \Ap/(2B_0M^2)$.
-From our numerical solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
-$2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
-which is about $\approx 5\%$ lower than the simulation result (Figure 3 of \cite{East2018}),
+From our numerical solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with
+the BH spin and approaches $2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
+which is about $\approx 5\%$ lower than the simulation result (Figure 3 in Ref. \cite{East2018}),
 while the angular velocity $\Omega$ as a function
@@
 or our numerical solutions, while the solid lines are corresponding polynomial
-fitting curves which we require to approach Eq.(\ref{eq:lowEdot}) for small
+fitting curves which we require to approach Equation (\ref{eq:lowEdot}) for small
 spins and to be flat for extremal spins. As expected, our energy extraction
@@
 equatorial current sheet, which contribute about half of the total BZ flux for extremal spins in
-the case of vertical field lines.
+the case of uniform field configuration.
 
 Due to the resemblance of the vertical field configuration and general parabolic field configurations,
-it is natural to expect an equatorial current develops within the ergosphere,
+it is reasonable to expect an equatorial current develops within the ergosphere,
 where the magnetic dominance loses, therefore the marginally force-free boundary
-condition (\ref{eq:bc3}) should also be a good work approximation here.
+condition (\ref{eq:bc3}) should also be a good work approximation for studying
+the BH magnetosphere structure with parabolic magnetic field lines.
 It is straightforward to solve the GS equation and self-consistently
@@
 
-Numerical solutions for the general parabola field configuration are out of scope of this paper.
-The analysis of Section \ref{subsec:features} which is based on the radiation condition
-and the marginally force-free equatorial boundary condition.
+Though we do not numerically solve the GS equation for the general parabolic field configurations,
+the qualitative properties we summarized in Section \ref{subsec:features} also apply here,
+since they are dictated by the radiation condition and the marginally force-free equatorial boundary condition,
+and are independent of the GS equation.
 
@@
 properties discussed in Section \ref{subsec:features} also apply here, since they are dictated by
-the radiation condition and the marginally force-free boundary condition, and GS equation only
+the radiation condition and the marginally force-free boundary condition, while the GS equation only
 serves to quantify these properties.

### 2018-07-03 paper/ms.tex
save

@@
  \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)
- +\frac{\Sigma}{\Delta}I^2\right]
+ +\frac{\Sigma}{\Delta}I^2\right] .
 \end{aligned}
@@
 
-The numerical algorithm for searching desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$
+The numerical algorithm of searching for the desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$
 is detailed in the following steps.
 
-1. We choose an initial guess for the field configuration, functions
+1. We choose an initial guess for the field configuration, eigenfunctions
 $\{ \Omega(\Ap), I(\Ap)\}$
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-which explicitly displays the features we anticipated in Section \ref{subsec:features} and is consistent with
-the simulation results \cite{East2018}.
+which explicitly displays the features we anticipated in Section \ref{subsec:features} and agrees with
+the simulation results in detail \cite{East2018}.
 
@@
 while the angular velocity $\Omega$ as a function
-of normalized magnetic flux $\Ap/\AEE$ shows a good agreement with the simulation results.
+of normalized magnetic flux $\Ap/\AEE$ is in agreement with the simulation results to high precision.
 
@@
 \includegraphics[scale=0.7]{f2b}
-\caption{\label{fig:omega} Upper panel: the angular velocity  $\Omega(\Ap)$ for different BH spins.
+\caption{\label{fig:omega} Upper panel: the angular velocity  $\Omega(\Ap)$ for different BH spins
+obtained from our numerical solutions.
 Lower Panel: comparison of our numerical results (solid lines) with the simulation results of
-Ref. \cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
+Ref.\cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
 dash-dotted lines.}
@@
 
+To summarize, the uniform field solution is indeed unique as double confirmed by the high-accuracy FFE
+simulations and by our numerical solutions, where the radiation condition and the marginally force-free
+equatorial boundary condition largely shape the  structure of the BH magnetosphere.
+
 \section{Discussion}
@@
 \subsection{Application to general field configurations}
-In real astrophysical environment, we expect the field lines are more close to parabolas instead of
-being strictly vertical. In many previous studies of such field
+In real astrophysical environment, we expect the field lines far away from the central BH
+are more close to parabolas instead of being strictly vertical. In several previous studies of such field
 configurations \cite[e.g.][]{Tchekhovskoy2010,Nathanail2014,Mahlmann2018},
@@
 
-Due to the resemblance of the vertical field configuration and general parabolic field configurations,
+Due to the resemblance of near-horizon field lines in the two cases,
 it is reasonable to expect an equatorial current develops within the ergosphere,
@@
 the qualitative properties we summarized in Section \ref{subsec:features} also apply here,
-since they are dictated by the radiation condition and the marginally force-free equatorial boundary condition,
-and are independent of the GS equation.
+since these properties are the consequence of the radiation condition and the marginally force-free equatorial boundary condition,
+while the GS equation only serves to quantify them.
 
-\subsection{Near-horizon field configuration}
+\subsection{Near-horizon magnetic field lines}
 In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
@@
 where the function $F(\Ap)$ is of $\mathcal O(\Ap)$ and  is field configuration dependent. The basic logic is:
-$\Omega$ must be nonzero for all field lines entering the ergosphere due to the static limit; as a result, $I$ must be nonzero
-for these field lines. If there is field line crossing the equator, the electric current either flows. Then
-the charge conservation is violated (if there exists no current sheet).
+$\Omega$ must be nonzero for all field lines entering the ergosphere due to the frame-dragging effect;
+as a result, $I$ must be nonzero for these field lines. If there is field line crossing the equator,
+the electric current either flows. Then the charge conservation is violated (if there exists no current sheet).
 
@@
 around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface
-must intersect the event horizon or end up on the equatorial current sheet".
+must intersect the event horizon or end up on the equatorial current sheet". Specifically,
+this claim excludes the existence of field lines entering the ergosphere and crossing the
+equator vertically.
 
@@
 
-In realistic astrophysical environment, we expect the magnetic field lines are more close to
-parabolas instead of being strictly vertical. Due to the resemblance, we also expect the marginally
-force-free equatorial boundary condition to be a good working approximation. Though we do not
-numerically solve the GS equation for the parabolic configuration in this paper, the qualitative
-properties discussed in Section \ref{subsec:features} also apply here, since they are dictated by
-the radiation condition and the marginally force-free boundary condition, while the GS equation only
-serves to quantify these properties.
+In realistic astrophysical environment, we expect the magnetic field lines far away from the central BH
+are more close to parabolas instead of being strictly vertical. However, we also expect the marginally
+force-free equatorial boundary condition to be a good working approximation for the parabolic field configurations,
+due to the resemblance of the near-horizon field configurations in the two cases.
+Though we do not numerically solve the GS equation for the parabolic configurations in this paper, the qualitative
+properties of the uniform field solution summarized in Section \ref{subsec:features} also apply here,
+since these properties are dictated by the radiation condition $I = \Omega \times \mathcal F(\Ap)$
+and the marginally force-free boundary condition $B^2-E^2=0$, while the GS equation only serves to quantify them.
 
 \acknowledgements
-
-This research was supported by Perimeter Institute for Theoretical Physics.
+ZP was supported by the UC Davis Dissertation Year Fellowship when this work was started.
+This research was also supported by Perimeter Institute for Theoretical Physics.
 Research at Perimeter Institute is supported by the Government of Canada

### 2018-07-03 paper/ms.tex
save

@@
     the equatorial current sheet
-    within the ergosphere for asymptotic uniform field. For the latter, the equatorial boundary
+    within the ergosphere for asymptotic uniform field configuration. For the latter, the equatorial boundary
     condition is well approximated being marginally force-free, i.e., $B^2-E^2\approx 0$, where $B$ and
-    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit uniform field
+    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit the uniform field
     solution to the Kerr BH magnetosphere structure and investigate the role of the marginally force-free
-    equatorial boundary condition in the BH magnetosphere structure.  We find the major qualitative properties of the magnetosphere structure are attributed
-    to the marginally force-free condition without invoking the Grad-Shafranov (GS) equation which governs the structure of
-    the force-free magnetosphere in steady state. We propose an algorithm
-    for numerically solving the GR Grad-Shafranov equation and self-consistently imposing the marginally force-free equatorial
-    condition, and we find a good agreement between our numerical solutions and the high-accuracy FFE simulations.
-    We also discuss the applicability of this boundary condition and the numerical algorithm proposed
-    in this paper for general magnetic field configurations.
+    equatorial boundary condition.  We find this boundary condition plays an important role in
+    shaping the BH magnetosphere in various aspects, including the shape of the light surface, the near-horizon field
+    line configuration and the source of the Poynting flux.
+    We also propose an algorithm for numerically solving the GR Grad-Shafranov equation and self-consistently imposing the marginally force-free equatorial
+    condition. As a result, we find a good agreement between our numerical solutions and the high-accuracy FFE simulations.
+    We also discuss the applicability of the marginally force-free boundary condition and the numerical algorithm for general magnetic field configurations.
 \end{abstract}
@@
 configuration as an example, the solutions obtained from different approaches
-are in quantitative agreement,  see e.g.\cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004}
+are in quantitative agreement,  see e.g. \cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004}
 for general relativistic magnetohydrodynamic simulations,
@@
 But for other magnetic field configurations, there is no such good agreement, e.g.,
-different approaches do even reach a consensus on the solution uniqueness for uniform field configuration.
+different approaches do not even reach a consensus on the solution uniqueness for the uniform field configuration.
 Several force-free electrodynamics (FFE) simulation \cite{Komissarov2004e, Komissarov2005,
-Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017} have been done,
+Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017} have been done and
 the BH magnetospheres in these simulations all settle down to a steady state with similar final field configuration,
 which is an indicator for solution uniqueness.
-However, a family of analytic solutions were presented for slowly spinning BHs \cite{Yang2015, Pan2017}.
-But no instability mode was found for these solutions \cite{Yang2015}, therefore the solution stability
+However, a family of analytic solutions were presented for slowly spinning BHs,
+and no instability mode was found for any of these solutions \cite{Yang2015}. Therefore the solution stability
 is not likely the explanation for the solution uniqueness.
@@
 From the viewpoint of numerical solutions, the structure of a BH magnetosphere in axisymmetric and
-steady state is governed by the GS equation, which is a second-order differential equation of
-the magnetic flux $\Ap(r,\theta)$, with two eigenfunctions $I(\Ap)$ and $\Omega(\Ap)$ to be self-consistently
-determined by requiring the magnetic field line smoothly cross the light surfaces (LSs).
-But for the uniform field configuration, there is only one LS, which is insufficient for determining
-the two eigenfunctions. Consequently there should exist infinitely many solutions \cite{Nathanail2014}.
+steady state is governed by the Grad-Shafranov (GS) equation, which is a second-order differential equation of
+the magnetic flux $\Ap(r,\theta)$, with two eigenfunctions $I(\Ap)$ and $\Omega(\Ap)$ to be
+determined. For common field configurations, the two eigenfunctions are determined by requiring the
+magnetic field line smoothly cross the light surfaces (LSs), where the GS equation degrades to be first-order.
+But for the uniform field configuration, there exits only one LS, which is insufficient for determining
+the two eigenfunctions. Following this argument, there should exist infinitely many solutions \cite{Nathanail2014}.
 
@@
 proposed that the two eigenfunctions are connected by the radiation condition at infinity instead of
-being independent, which was confirmed by recent FFE simulations done
+being independent, which was readily confirmed by recent FFE simulations done
 by East and Yang \cite{East2018}. In addition, there are other interesting features in the structure of the BH
@@
 In Section \ref{sec:uni_sol}, we clarify the radiation condition, boundary conditions and numerical algorithm
-for the uniform field solution. In Section \ref{sec:discussion}, we discuss the application
-to general field line configurations and near-horizon
-field line configuration. Summary is given in Section \ref{sec:summary}.
+for the uniform field solution. In Section \ref{sec:discussion}, we generalize the discussion
+to  more field configurations. Summary is given in Section \ref{sec:summary}.
 
@@
 \een
-with $\mathcal K(r,\theta; \Omega )= \left[\frac{\beta}{\Sigma}\Omega^2 \sst
+where the LS function
+\be
+\label{eq:ls}
+\mathcal K(r,\theta; \Omega )= \frac{\beta}{\Sigma}\Omega^2 \sst
 -\frac{4ra}{\Sigma}\Omega \sst
--\left(1-\frac{2r}{\Sigma}\right)\right]$ being the LS function,
+-\left(1-\frac{2r}{\Sigma}\right)\right,
+\ee
 $\mu\equiv\ct$,  and  the primes designate  derivatives with respect to $A_\phi$.
@@
 \subsection{Solution uniqueness and radiation condition}
-For common field configurations, including split monopole and parabola, there exist two LSs where
+For common field configurations, there exists two LSs where
 the LS function vanishes and the GS equation degrades from second order to first order. As proposed
@@
 $\{\Omega(\Ap), I(\Ap), \Ap(r,\theta)\}$  is uniquely found. But for the vertical field lines, their
-exist only one LS, which is insufficient to determine two eigenfunctions.
-Therefore many solutions are expected \cite{Nathanail2014, Mahlmann2018} but the many-solutions scenario is in
-conflict with several previous FFE simulations.
+exists only one LS, which is insufficient for determining two eigenfunctions.
+Therefore many solutions are expected \cite{Nathanail2014, Mahlmann2018}, but the many-solutions scenario is in
+conflict with several previous FFE simulations \cite{Komissarov2004e, Komissarov2005,
+Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017}.
 To tackle this problem,  Pan et. al. \cite{Pan2016a, Pan2017} proposed that the two eigenfunctions are not independent;
@@
 which has been readily confirmed by recent high-accuracy FFE simulations \cite{East2018}.
+Combining with suitable boundary conditions, we expect a unique uniform field solution as indicated
+by the previous FFE simulations.
 
@@
 where $r_+$ is the radius of the event horizon,
-while the equatorial boundary conditions are more unclear until recent simulations \cite{East2018}
+while the equatorial boundary condition is more uncertain until recent simulations \cite{East2018}
 come out which show that there exists an equator current sheet within the ergosphere where the
-magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$. Motivated by these simulations,
+magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$. Motivated by the simulation results,
 we choose the following equatorial boundary condition in our numerical solutions,
@@
 which involves both derivatives $\Am$ and $\Ar$ on the boundary.
-Therefore, it is numerically non-trivial to impose this boundary condition in computation.
+As we will see later, it is numerically non-trivial to impose this boundary condition in computation.
 
@@
 in our computation, as a proxy of the marginally force-free equatorial boundary condition (\ref{eq:bc3}),
-where $\AHE$ and $\AEE$ are the magnetic flux entering the horizon and the ergosphere, respectively;
+where $\AHE$ and $\AEE$ are the magnetic flux enclosed by the horizon and by the ergosphere, respectively;
 ``HE" and ``EE" are short for Horizon-Equator and Ergosphere-Equator, respectively.
-For definiteness, we choose $B^2+E^2$ to be the energy density measured by the zero-angular-momentum-observers.
+For definiteness, we choose $B^2+E^2$ to be the energy density measured by zero-angular-momentum-observers.
 Explicitly, we have
@@
 Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
-From the expression of the LS function, it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
+From the expression of the LS function (\ref{eq:ls}), it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
 On this point,  the LS function $\mathcal K$ vanishes,
@@
 must be non-zero inside the ergosphere.  Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$, i.e.
-to satisfy the boundary condition (\ref{eq:bc3}), the LS must interact the equator at $r=2$, which also
+to satisfy the boundary condition (\ref{eq:bc3}), the LS must intersect the equator at $r=2$, which also
 justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) .
@@
 
-The numerical algorithm of searching for the desired $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$
+The numerical algorithm of searching for the desired eigenfunctions and the equatorial
+boundary condition $\{\Omega(A_\phi), I(A_\phi), \Am(\mu =0, r_+\leq r \leq 2)\}$
 is detailed in the following steps.
@@
 $\{ \Omega(\Ap), I(\Ap)\}$
-and equatorial boundary condition of Neumann type as follows
+and equatorial boundary condition  as follows
 \begin{subequations}
@@
 \subsection{Near-horizon magnetic field lines}
-In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
-around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event horizon",
-based on the radiation condition $I = \Omega \times \mathcal F(\Ap)$ and the assumption of no current sheet within the ergosphere,
-where the function $F(\Ap)$ is of $\mathcal O(\Ap)$ and  is field configuration dependent. The basic logic is:
+In a previous study \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
+around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event horizon".
+This claim is based on the radiation condition
+\be
+\label{eq:Grad}
+I = \Omega \times \mathcal F(\Ap),
+\ee
+and the assumption of no current sheet within the ergosphere,
+where the function $\mathcal F(\Ap)$ is of $\mathcal O(\Ap)$ and  is field configuration dependent.
+The basic logic for obtaining the claim is as follows.
 $\Omega$ must be nonzero for all field lines entering the ergosphere due to the frame-dragging effect;
-as a result, $I$ must be nonzero for these field lines. If there is field line crossing the equator,
-the electric current either flows. Then the charge conservation is violated (if there exists no current sheet).
+as a result, $I$ must be nonzero for these field lines according to the radiation condition.
+If there is field line entering the ergosphere and crossing the equator, the electric current either flows
+towards the equator from both the $+z$ and $-z$ side, or flows away from the equator to infinity in
+both the $+z$ and $-z$ direction. For each case, the charge conservation is violated
+if there exists no equatorial current sheet.
 
-However, simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
+However, the FFE simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
 the force-free condition breaks down. Therefore the above claim should be generalized as
@@
 the GS equation, which is a second-order differential equation about the magnetic flux $\Ap$, with two
-free functions $\Omega(\Ap)$ and $I(\Ap)$ to be determined by . For the uniform field configuration, there is only one
+eigenfunctions $\Omega(\Ap)$ and $I(\Ap)$ to be determined. For common field configurations, there exists
+two LSs on which the GS equation degrades to be first-order, and the two eigenfunctions are determined
+by the requirement that magnetic field lines should smoothly cross the two LSs.
+For the uniform field configuration, there is only one
 LS, which is insufficient for determine both  $\Omega(\Ap)$ and $I(\Ap)$.
-Therefore the solution uniqueness has been a controversial problem.
-Recent high-accuracy force-free simulations done in Ref. \cite{East2018}
-undoubtedly show that the two functions are not independent;
-instead they are related by the radiation condition (\ref{eq:rad}).
-In addition, an equatorial current sheet within the ergosphere was readily confirmed
-in the simulations
+Therefore the solution uniqueness of the uniform field configuration has been a controversial problem.
+To tackle this problem, we  proposed that the two functions are related by the radiation condition (\ref{eq:rad}),
+instead of being independent \cite{Pan2017}, which was readily confirmed by recent high-accuracy
+FFE simulations \cite{East2018}. In these simulations, an equatorial current sheet
+develops within the ergosphere and the magnetic dominance marginally loses, i.e. $B^2-E^2\approx 0$.
 
-In this paper, we revisit the problem of the uniform field solution.
+Motivated by these simulations, we revisit the problem of the uniform field solution in this paper.
 We find the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
@@
 in various aspects, including the shape of the LS, the near-horizon field line configuration and
-source of BZ flux (see Section \ref{subsec:features} for details). We also propose an algorithm
-for numerically solving the GS equation and consistently imposing the marginally force-free
-equatorial boundary condition. As a result, we find a good agreement between our numerical solutions
-with the high-accuracy FFE simulations.
+the source of BZ flux (see Section \ref{subsec:features} for details). Other than these qualitative properties,
+we also propose an algorithm for numerically solving the GS equation and consistently imposing
+the marginally force-free equatorial boundary condition. As a result, we find a good agreement
+between our numerical solutions with the high-accuracy FFE simulations.
 
@@
 properties of the uniform field solution summarized in Section \ref{subsec:features} also apply here,
-since these properties are dictated by the radiation condition $I = \Omega \times \mathcal F(\Ap)$
-and the marginally force-free boundary condition $B^2-E^2=0$, while the GS equation only serves to quantify them.
+since these properties are dictated by the radiation condition
+and the marginally force-free boundary condition, while the GS equation only serves to quantify them.
 

### 2018-07-05 paper/anl3.tex

\documentclass[iop,apj]{emulateapj}
\usepackage{amsmath,amssymb, amsthm,amstext}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{array}
\usepackage{bm}
\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}

\newtheorem{claim}{Claim}

\bibliographystyle{apj}

% Shorts
\def\nn{\nonumber}
\def\st{\sin\theta}
\def\ct{\cos\theta}
\def\sst{\sin^2\theta}
\def\cct{\cos^2\theta}
\def\Ar{A_{\phi,r}}
\def\Arr{A_{\phi,rr}}
\def\Am{A_{\phi,\mu}}
\def\Amm{A_{\phi,\mu\mu}}
\def\Ah{A_{\phi,\theta}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ben{\begin{eqnarray}}
\def\een{\end{eqnarray}}
\def\WH{\Omega_{\rm H}}
\def\A0{A_{\phi}^{(0)}}
\def\e{{\bf e}}
\def\AB{A_\phi^{\rm H}}
\def\tL{\tilde{\mathcal L}}

\def\Alfven{Alfv\`en}

% Journals

% Authors
\begin{document}
\title{Analytic properties of force-free jets in the Kerr spacetime -- III:\\
uniform field solution}

\slugcomment{Submitted to \apj}

\author{Zhen Pan}
\affil{Department of Physics, University of California, One Shields Avenue, Davis, CA 95616, USA;
\ {\textcolor{blue}{zhpan@ucdavis.edu}}}
%\email{zhpan@ucdavis.edu}

\author{Cong Yu}
\affil{Yunnan Observatories, Chinese Academy of Sciences, Kunming 650011, China; \ {\textcolor{blue}{cyu@ynao.ac.cn}}\\
Key Laboratory for the Structure and Evolution of Celestial Objects, Chinese Academy of Sciences, Kunming 650011, China;}
%\email{cyu@ynao.ac.cn}

\author{Lei Huang}
\affil{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical Observatory, \\
Chinese Academy of Sciences, Shanghai, 200030, China; \ {\textcolor{blue}{muduri@shao.ac.cn}} }

\shorttitle{Analytic properties of force-free jets in the Kerr spacetime }
\shortauthors{Z. Pan, C. Yu and L. Huang}

\begin{abstract}
The structure of steady axisymmetric force-free magnetosphere of a Kerr black hole (BH) is governed
by a second-order partial differential equation of $A_\phi$ depending on two ``free" functions
$\Omega(A_\phi)$ and $I(A_\phi)$, where $A_\phi$ is the $\phi$ component of the vector
potential of the electromagnetic field, $\Omega$ is the angular velocity of the magnetic
field lines and $I$ is the poloidal electric current.
In this paper, we investigate the solution uniqueness.
Taking asymptotically uniform field as an example, analytic studies imply that
there are infinitely many solutions approaching uniform field at infinity,
while only a unique one is found in general relativistic magnetohydrodynamic simulations.
To settle down the disagreement, we reinvestigate the structure of the governing equation
and numerically solve it with given constraint condition and boundary condition.
We find that the constraint condition
(field lines smoothly crossing the light surface (LS))
and boundary conditions at horizon and at infinity
are connected via radiation conditions at horizon and at infinity, rather than being independent.
With appropriate constraint condition and boundary condition, we numerically solve the governing equation
and find a unique solution. Contrary to naive expectation,
our numerical solution yields a discontinuity in the angular velocity of the field lines
and a current sheet along the last field line crossing the event horizon.
We also briefly discuss the applicability of the perturbation approach to solving the governing equation.
\end{abstract}

\keywords{gravitation -- magnetic field -- magnetohydrodynamics}

\bigskip\bigskip

\section{Introduction}
The Blandford-Znajek (BZ) mechanism \citep{Blandford1977} is believed to be one of most efficient ways
to extract rotation energy from spinning black holes (BHs), which operates in BH
systems on all mass scales, from the stellar-mass BHs of gamma ray bursts to the
supermassive BHs of active galactic nuclei. In the past decade, we have gained
better understanding of the BZ mechanism from general relativistic
magnetohydrodynamic (GRMHD) simulations \citep[e.g.][]{Komissarov2001, Komissarov2004e,
Komissarov2004, Komissarov2005, Semenov2004, McKinney2004, McKinney2005, McKinney2007a,
McKinney2007b, Komissarov2007, Tchekhovskoy2008, Tchekhovskoy2010, Tchekhovskoy2011,
Nagataki2009, Nagataki2011, Palenzuela2011, Alic2012, Tchekhovskoy2012, Penna2013, McKinney2013}, numerical
solutions \citep[e.g.][]{Fendt1997, Udensky2004, Udensky2005, Palenzuela2010,
Contopoulos2013, Nathanail2014} and analytic perturbation solutions \citep[e.g.][]{Tanabe2008,
Beskin2013, Pan2014, Pan2015b, Pan2015, Pan2016, Gralla2014, Gralla2015, Gralla2016a,
Yang2015, Penna2015} to the steady axisymmetric force-free electrodynamics in the Kerr
spacetime.\footnote{A few families of exact solutions \citep[e.g.][]{Menon2005, Menon2007,
Menon2011, Brennan2013, Menon2015, Compere2016} to the equations of force-free electrodynamics
in the Kerr spacetime  have been found in the past decade. But these solutions
have various limitations, e.g., not allowing energy extraction from the BH,
being electrically dominated instead of magnetically dominated, lacking clear
physical interpretation, or being time-dependent and not axisymmetric, which
make it difficult to compare these exact solutions with simulations and
numerical solutions.} Various studies converge to a common picture of how the BZ mechanism operates:
The spinning BH distorts the poloidal magnetic field $\bm{B_{\rm P}}$, and induces the poloidal electric field $\bm{E_{\rm P}}$
and toroidal magnetic field $\bm{B_{\rm T}}$,
which generate an outward Poynting flux $\bm{E_{\rm P}
\times B_{\rm T} }$  along the magnetic field lines threading the spinning BH.
The rotation energy of the spinning BHs is extracted in the form of Poynting flux
\citep{Komissarov2009, Beskin2010}.

To step further, it is natural to ask whether
these different approaches give qualitatively and quantitatively consistent
descriptions of the BH magnetosphere structure, e.g.,
the topology of magnetic fields, the electric current distributions,
the angular velocities of the magnetic field lines
and the energy extraction rates. The answer is {\em yes} and {\em no}. The axisymmetric, steady-state,
force-free magnetosphere around  Kerr BHs is governed by the
general relativistic Grad-Shafranov (GS) equation. For
the simplest magnetic field configuration, split monopole
field, both analytic \citep{Pan2015b} and numerical solutions \citep{Nathanail2014}
reproduce the simulated angular velocity of field lines $\Omega$,
poloidal electric current $I$ and energy extraction rate $\dot E$ to high precision
\citep{Tchekhovskoy2010}. But for the asymptotically
uniform field, different approaches do not even reach a consensus on the solution uniqueness.
Time-dependent simulations \citep[e.g.][]{Komissarov2005, Komissarov2007, Yang2015} seem to converge to
a unique solution. Previous analytic studies \citep{Beskin2013, Pan2014, Gralla2016a} seem to find a unique
perturbation solution which roughly agrees with GRMHD simulations.
But in this paper, we will show there are actually many of them
due to the superposition of monopole component (and other possible components).
According to the argument of \citet{Nathanail2014},
solving the GS equation is actually an eigenvalue
problem, with two eigenvalues $\Omega(A_\phi)$ and $I(A_\phi)$ to be determined
by requiring field lines to smoothly cross the light surfaces (LSs).
For common field configurations, there exists usually two LSs, sufficing to determine two eigenvalues.
With only one LS for the uniform field configuration and one more boundary condition,
\citet{Nathanail2014} numerically found a unique solution, which however shows distinctive features from
previous GRMHD simulations \citep{Komissarov2005}.

How to explain the relationship between the unique solution
and the infinitely many possible candidates, and the discrepancy between
previous numerical solution and GRMHD simulations?
\footnote{It is definitely worthwhile examining the solution uniqueness problem of
the BZ mechanism, considering its significance in the modern relativistic astrophysics.
For example, rotating BHs are believed to be described by Kerr solution, but there is
no solid evidence for it. Some efforts have been done to detect possible deviation from Kerr solution
via BZ mechanism powered jet emission \citep[e.g.][]{Bambi2012b, Bambi2012, Bambi2015, Pei2016}.
A prerequisite for these BZ applications is its solution uniqueness.}
Does the plasma inertia make a difference? The force-free condition is assumed in
both analytic and numerical solutions, but the inertia cannot be completely
ignored in simulations. Taking account of the plasma inertia, \citet{Takahashi1990}
proposed the so-called MHD Penrose process, where the plasma particles within the
ergosphere are projected onto negative-energy orbits by magnetic field and
eventually are captured by the central BH. As a result,  \Alfven\ waves are
generated along the magnetic field lines, and BH rotation energy is carried away
by these \Alfven\ waves. \citet{Koide2002} and \citet{Koide2003} found the
MHD Penrose process was operating in GRMHD simulations (see \citealp[e.g.][]{Lasota2014,
Koide2014,Toma2014,Kojima2015,Toma2016}  for recent discussions on this issue).
If the MHD Penrose process is the dominant energy extraction process, the unique
solution found in simulations actually describes the MHD Penrose process instead
of the BZ mechanism. However, later simulations showed that the MHD Penrose process
is only a transient state, after which the \Alfven\ waves decay, the system settles
down into a steady state, and the BZ mechanism takes over \citep[e.g.][]{Komissarov2005}.
Therefore the plasma inertia seems to make little difference after the system settles
down into the steady state.

Another possible explanation is that, among all these mathematically possible
solutions, only the one found simulations is stable.
\citet{Yang2014} and \citet{Yang2015} analyzed the stability of these solutions,
and no unstable mode was found at order $O(a)$, where $a$ is the dimensionless
BH spin. Therefore modes can be unstable with a growth rate at $\sim O(a^2)$
at most.\footnote{The stability problem of general force-free jets is a complicated story.
Early studies implied that the force-free jets are vulnerable to various instabilities
\citep[e.g.][]{Begelman1998,Lyubarskii1999, Li2000, Wang2004}
while later studies showed that these instabilities are strongly suppressed by
field rotation, poloidal field curvature, etc
\citep[e.g.][and references therein]{Tomimatsu2001, McKinney2009a, Narayan2009g}.}
But the relevant timescale is
much longer than the  transient time scales observed in simulations.  Therefore
they concluded that the selection rule unlikely comes from instability.

In this paper, we show that the uniform field solution is
unique as strongly implied by previous GRMHD simulations
and pointed out by \citet{Nathanail2014}.
Following the algorithm proposed by \citet{Contopoulos2013} and \citet{Nathanail2014},
we numerically find a unique combination of $\Omega$ and $I$,
ensuring both smooth field lines across the LS and uniform field at infinity.
Contrary to \citet{Nathanail2014}, our numerical solution yields a discontinuity in the angular velocity of
field lines and a current sheet along the last field line crossing the event horizon,
which are features found in previous simulations.

We also investigate the applicability of analytic perturbation approach to the GS equation,
which relies on a fixed unperturbed solution and priorly known asymptotic behavior of magnetic field.
Analytic approach breaks down if any of the two factors is violated.
Both of the two are satisfied for monopole field in Kerr spacetime,
therefore we see the perfect match between high-order perturbation solutions,
and results from simulations and numerical solutions.
But for the uniform field, the unperturbed background field is not fixed due to
the superposition of the monopole component, therefore the perturbation approach
cannot predict a unique solution.

The paper is organized as follows. In Section \ref{sec:basic},
we summarize the basic equations governing the steady axisymmetric force-free magnetospheres.
In Section \ref{sec:sketch}, we clarify the relation between constraint conditions, radiation
conditions and boundary conditions; and our numerical method to solve the GS equation.
We apply the perturbation approach on the uniform field problem
and clarify the applicability of analytic perturbation approach in Section \ref{sec:pert}.
Summary and Discussions are given in Section \ref{sec:disc}. In Appendix, we present a robust solver
for the horizon regularity condition and its implication for the existence of electric current.

\section{basic equations}
\label{sec:basic}
In the force-free approximation, electromagnetic energy greatly exceeds that of matter.
Consequently, the force-free magnetospheres is governed by energy
conservation equation of electromagnetic field, or
conventionally called as the GS equation. In the Kerr spacetime,
the axisymmetric and steady
GS equation is written as \citep{Pan2014}
\ben
\label{eq:GS}
&-&\Omega \left[(\sqrt{-g}F^{tr})_{,r} +
(\sqrt{-g}F^{t\theta})_{,\theta} \right] + F_{r\theta}I'(A_\phi) \nn\\
&&+ \left[(\sqrt{-g}F^{\phi r})_{,r} +
(\sqrt{-g}F^{\phi\theta})_{,\theta} \right] = 0 \ ,
\een
which expands as
\citep[see also e.g.][in slightly different forms]{Contopoulos2013, Nathanail2014, Pan2016}
\ben
\label{eq:GSe}
&&\phantom{+}
 \left[\frac{\beta}{\Sigma}\Omega^2 \sst
-\frac{4ra}{\Sigma}\Omega \sst
-\left(1-\frac{2r}{\Sigma}\right)\right] \Arr  \nn\\
&&
+\left[\frac{\beta}{\Sigma}\Omega^2 \sst
-\frac{4ra}{\Sigma}\Omega \sst
-\left(1-\frac{2r}{\Sigma}\right)\right] \frac{\sst}{\Delta } \Amm \nn \\
&&
+ \left[  \Omega^2 \sst\left(\frac{\beta}{\Sigma}\right)_{,r}
-\Omega\sst\left(\frac{4ra}{\Sigma}\right)_{,r}
+\left(\frac{2r}{\Sigma}\right)_{,r}\right] \Ar \nn\\
&&
+\left[ \Omega^2\left( \frac{\beta\sst}{\Sigma} \right)_{,\mu}
-\Omega\left(\frac{4ra\sst}{\Sigma}\right)_{,\mu}
+\left(\frac{2r}{\Sigma}\right)_{,\mu}\right]\frac{\sst}{\Delta}\Am \nn \\
&&
+ \left[ \left(\frac{\beta}{\Sigma}\right) \Omega-\frac{2ra}{\Sigma}\right]
\sst\Omega'\left(\Ar^2 + \frac{\sst}{\Delta}\Am^2\right) \nn\\
&&
- \frac{\Sigma}{\Delta} II' = 0 \ ,
\een
where $\Sigma = r^2 + a^2 \mu^2$, $\Delta = r^2 -2r + a^2$, $\beta = \Delta\Sigma + 2r(r^2 + a^2)$,
$\mu\equiv\ct$ and  the primes designate  derivatives with respect to $A_\phi$.
For clarity, we may write the GS equation in a more illustrating form
\ben
\label{eq:GSg}
&&\phantom{+}
 \left[\Arr + \frac{\sst}{\Delta}\Amm \right]  \mathcal K(r,\theta; \Omega )\nn \\
&&
+\left[\Ar \partial_r^\Omega  +  \frac{\sst}{\Delta}\Am \partial_\mu^\Omega\right] \mathcal K(r,\theta; \Omega ) \nn \\
&&
+ \frac{1}{2}\left[\Ar^2 + \frac{\sst}{\Delta}\Am^2\right]  \Omega' \partial_\Omega \mathcal K(r,\theta; \Omega )\nn \\
&&
- \frac{\Sigma}{\Delta}II' = 0 \ ,
\een
where $\mathcal K(r,\theta; \Omega )$ is the prefactor of $\Arr$ in Equation~(\ref{eq:GSe}),
$\partial_i^\Omega (i=r, \mu)$  denotes the partial derivative
with respect to coordinate $i$ with $\Omega$ fixed, and $\partial_\Omega$ is the derivative with
respect to $\Omega$. The GS equation written in this compact form manifests clear symmetry,
therefore is beneficial in various aspects.\footnote{
For example, in flat spacetime, the classical pulsar
equation \citep{Scharlemann1973} is recovered by plugging
$\mathcal K(r,\theta; \Omega ) = \Omega^2 r^2\sst - 1$ into Equation~(\ref{eq:GSg}).}

\section{the solution uniqueness problem}
\label{sec:sketch}

% \citet{Contopoulos2013} and  \citet{Nathanail2014} proposed that solving the
% GS equation is an eigenvalue problem with eigenfunction
% $A_\phi$ and eigenvalues $I$ and $\Omega$ to be determined. To solve
% the GS equation self-consistently, eigenvalues $I$ and $\Omega$
% were adjusted to make magnetic field lines smoothly cross the {\em two}
% LSs. In this way, they confirmed the results of previous
% simulations for asymptotically monopole magnetic field.
% But for the asymptotically uniform magnetic field, the
% field lines crossing the event horizon only cross {\em one} LS
% (the ILS), which is not sufficient for determining the {\em two}
% eigenvalues $I$ and $\Omega$. {\bf To uniquely determine the solution, we need one more condition.}

In this section, we first clarify all the constraint conditions the GS equation satisfies,
and their relation with boundary conditions at horizon and at infinity.
We find the constraint conditions and boundary conditions are not independent.
For a given $\Omega(A_\phi)$, we can numerically
find a $I(A_\phi)$ ensuring field lines smoothly crossing the LS, but the combination of
$\Omega(A_\phi)$ and $I(A_\phi)$ obtained this way usually is in conflict with the uniform field boundary
condition at infinity. To be consistent this boundary condition, $\Omega(A_\phi)$ and $I(A_\phi)$ must
satisfy one more constraint. Then, we numerically find the unique combination of $\Omega(A_\phi)$ and $I(A_\phi)$
ensuring field lines smoothly cross the LS and being consistent with the boundary condition at infinity.
Finally, we compare our numerical solution with previous studies.

\subsection{Constraint Conditions and Boundary Conditions}
We want physically allowed solutions to be finite and smooth everywhere.
At LS where $\mathcal K = 0$, the second-order GS equation degrades to a first-order equation
\be
\label{eq:ls}
\begin{aligned}
& \left[\Ar \partial_r^\Omega  +  \frac{\sst}{\Delta}\Am \partial_\mu^\Omega\right] \mathcal K(r,\theta; \Omega ) \\
&+  \frac{1}{2}\left[\Ar^2 + \frac{\sst}{\Delta}\Am^2\right]  \Omega' \partial_\Omega \mathcal K(r,\theta; \Omega)
= \frac{\Sigma}{\Delta}II'.
\end{aligned}
\ee
Field lines smoothly crossing the LS must satisfy the above constraint,
which we call LS crossing constraint condition. At horizon and infinity,
the requirement of solution finiteness leads to the radiation conditions \citep[e.g.][]{Pan2016},
which read as,
\be
\label{eq:znajek}
    I = \frac{2r(\Omega-\WH)\sst}{\Sigma} \Am \Big|_{r=r_+},
\ee
and
\be
\label{eq:infty}
    I = -\Omega\sst \Am \Big|_{r\rightarrow \infty},
\ee
where $\WH$ is angular velocity of the central BH.

But the radiation conditions and boundary conditions are not independent.
For example, the radiation condition (\ref{eq:znajek}) uniquely determines the boundary values at horizon
if $\Omega$ and $I$ are specified, and we will use it as the inner boundary condition in our numerical calculation.
In the same way, the radiation condition (\ref{eq:infty})
uniquely determines the boundary values at infinity, if $\Omega$ and $I$ are specified;
or the radiation condition (\ref{eq:infty}) enforces a constraint on $\Omega$ and $I$,
if the boundary condition at infinity is given.
In our working example, the boundary condition at infinity
\be
\label{eq:rinfty}
A_\phi(r\rightarrow\infty) = r^2\sst
\ee
is given. Plugging it into the radiation condition (\ref{eq:infty}), we find
that $\Omega$ and $I$ must satisfy a new constraint \citep{Nathanail2014, Pan2014, Pan2016}
\be
\label{eq:constr}
I = 2\Omega A_\phi.
\ee
Note that conditions (\ref{eq:infty}, \ref{eq:rinfty}, \ref{eq:constr}) are not independent,
and we will use two of them (\ref{eq:rinfty}, \ref{eq:constr}) to close the GS equation.

Now we get two constraint conditions (\ref{eq:ls}, \ref{eq:constr}),
and two boundary conditions in the $r$ direction  (\ref{eq:znajek}, \ref{eq:rinfty}) ready,
(where the inner boundary condition (\ref{eq:znajek}) is nontrivial, see Appendix for details).
The next step is to specify proper boundary conditions in the $\mu$ direction.
According to the claim proved in paper II:
\noindent {\it ``In the steady axisymmetric force-free magnetosphere
around a Kerr BH, all magnetic field lines that cross the
infinite-redshift surface must intersect the event horizon",}
\footnote{The claim depends on the relation $I\propto \Omega$,
which can be derived from the radiation condition at infinity [Equation (\ref{eq:infty})]. But their are some debates about
whether the radiation condition holds for vertical field configurations.
As for the uniform field,
there is no disagreement on the relation $I\propto \Omega$ [Equation (\ref{eq:constr})],
though \citet{Pan2016} interpreted it as the result of radiation condition,
while \citet{Nathanail2014} interpreted differently.}
\noindent the possible field configuration in the steady state is shown in the Figure 1 of paper II.
Consequently, we write  boundary conditions in
the $\mu$ direction as follows,
\be
\label{eq:tbc}
\begin{aligned}
A_\phi(\mu = 1) & = 0 , \\
A_\phi\left(\mu = 0, r_+\leq r\leq 2\right) &= \AB ,\\
\Am\left(\mu = 0, r\geq 2\right) &= 0 ,
\end{aligned}
\ee
where the horizon enclosed magnetic flux $\AB$ is to be determined self-consistently.

\subsection{Numerical Method and Results}
The algorithm for numerically solving the GS equation was proposed by
\citet{Contopoulos2013} and was optimized by \citet{Nathanail2014}.
We slightly tailor their algorithm to accommodate the problem we are working on.
We define a new radial coordinate $R = r/(1+r)$, confine our computation domain
$R\times \mu$ in the region  $[R(r_+), 1]\times [0,1]$,
and implement a uniform $512\times 64$ grid.
The detailed numerical steps are as follows:

1. We choose some initial guess $A_\phi$, trial functions $\Omega$ and $I$ as follows,
\footnote{The convergent solution is independent of the trial field configuration or the grid resolution.
For example, we tested different initial field configurations $A_\phi = r^2\sin^2\theta  +\epsilon (1-\cos\theta)$,
different initial trial functions $\Omega$ and $I$, and different grid resolutions.}
\be
\begin{aligned}
    A_\phi &= r^2\sin^2\theta, \\
    \Omega &= \frac{\WH}{2}\cos\left(\frac{\pi}{2}\frac{A_\phi}{\AB}\right),\\
    I &= \WH A_\phi\cos\left(\frac{\pi}{2}\frac{A_\phi}{\AB}\right).
\end{aligned}
\ee

2. We evolve $A_\phi$ using relaxation method \citep{Press1987},
while this method does not work properly at the LS due to the vanishing second order derivatives.
Fortunately, the directional derivative of $A_\phi$ is known as a function of $II'$ there (see Equation (\ref{eq:ls})).
We instead update $A_\phi$ at the LS using neighborhood grid points and the directional derivative.
From the directional derivative and the grid points on the left/right side,
we obtain $A_\phi(r_{\rm ILS}^-)$/$A_\phi(r_{\rm ILS}^+)$.
Usually the two are not equal and field lines are broken here. To smooth the field lines,
we adjust $I(A_\phi)$ and update $A_\phi(r_{\rm ILS})$ as follows:
\be
\begin{aligned}
    II'_{\rm new}(A_{\phi, \rm new}) &= II'_{\rm old}(A_{\phi, \rm old}) \\
    &- 0.02(A_\phi(r_{\rm ILS}^+) - A_\phi(r_{\rm ILS}^-)) \ ,
\end{aligned}
\ee
where
\be
    A_{\phi, \rm new} = 0.5(A_\phi(r_{\rm ILS}^+) + A_\phi(r_{\rm ILS}^-)) \ .
\ee
Usually, $II'$ obtained is not very smooth.
To refrain possible numerical instabilities, we fit $II'(A_\phi)$ with a eighth-order polynomials.
In addition, $II'$ consists of two pieces: a regular piece determined as described above,
and a singular piece (the current sheet part)
\be
-\int_0^{\AB} II' dA_\phi \ \delta(A_\phi-\AB) \ .
\ee
In our compuation, we model the delta function as a parabola confined in
a finite interval $[\AB, \AB (1+\delta)]$ with $\delta = 0.1$ \citep[see e.g.][]{Gruzinov2005}.

3. Repeat step 2 for $10$ times, then update $\Omega(A_\phi)$ according to the constraint (\ref{eq:constr}).

We iterate the initial guess solution following the above steps until field lines smoothly
cross the LS and satisfy the boundary conditions.
The numerical results are shown in Figure \ref{fig:lines}.
In the left panel, we show the convergent field configuration
which as expected matches those of simulations \citep[e.g.][]{Komissarov2007}.
In the right panel, we show functions $\Omega(A_\phi)$ and $II'(A_\phi)$.
From the plot, we see that the angular velocity of the last field line crossing the event horizon
$\Omega(\AB)$ is not vanishing, i.e., $\Omega(\AB) \simeq 0.28\WH$,
while we expect the angular velocity of field lines not crossing the BH vanishes,
i.e., $\Omega(A_\phi > \AB) = 0$.

\begin{figure*}
    \centering
\includegraphics[scale=0.45]{f1a}%
\includegraphics[scale=0.44]{f1b}
\caption{Left Panel: The magnetic field lines around a Kerr BH with spin $a=0.99$,
where the inner(solid)/outer(dashed) curve is the ILS/IRS.
Right Panel: Functions $\Omega(A_\phi)$ and $II'(A_\phi)$ of the uniform field configuration,
where the latter is normalized by the amount of field flux crossing the event horizon $\AB$.}
\label{fig:lines}
\end{figure*}

\subsection{Comparison with Previous Studies}

\citet{Nathanail2014} also studied BH magnetosphere structure of uniform field and concluded that
both $\Omega(A_\phi)$ and $I(A_\phi)$ must approach zero along the last field line crossing the event horizon,
and therefore the ILS coincides with the IRS along the equator,
and the electric current sheet does not appear. But as shown in the Appendix, the horizon regularity condition
requires the existence of current sheet along the equator. And our numerical solution shows that there is
a discontinuity in $\Omega(A_\phi)$ at $\AB$, and therefore the ILS lies between the event horizon
and the IRS, and there exists a current sheet.
The discrepancies here can be settled down by previous GRMHD simulations done by \citet{Komissarov2005},
where they observed a sharp transition in $\Omega(A_\phi)$ at $\AB$ and interpreted it as a discontinuity
smeared by numerical viscosity. It is worth noting that the discontinuity in $\Omega(A_\phi)$ does not lead to
any physical difficulties, e.g., the continuity of $\bm B^2- \bm E^2$ across the LS is not affected.

In addition, we do not explicitly show the BZ power of the uniform field configuration here,
because it is sensitive to the magnetic flux trapped by the event horizon $\AB$ which is boundary condition dependent.
In the real astrophysical environment, it is mainly determined by accretion process of the
central BH \citep[e.g.][]{Garofalo2009}.

\section{Applicability of Analytic Perturbation Approach}
\label{sec:pert}
In this section, we first recap the analytic perturbation approach to the GS equation,
then apply it to the uniform field problem \citep{Pan2014, Pan2015b} and explain
why this approach actually yields many solutions.
Finally, we discuss the applicability of the perturbation method.

We start with a unperturbed solution $A_0$ in the Schwarzschild spacetime,
\be
\label{eq:lgs}
\mathcal L A_0 =0,
\ee
where the operator
\be
\mathcal L\equiv\frac{\partial}{\partial
r}\left(1-\frac{2}{r}\right)\frac{\partial}{\partial r}
 +\frac{\sst}{r^2}\frac{\partial^2}{\partial \mu^2}.
\ee
For the corresponding Kerr metric solution $\{A_\phi, I(A_\phi), \Omega(A_\phi)\}$,
we assume $A_\phi|_{r\rightarrow\infty} = A_0$,
define $i = I|_{r\rightarrow\infty}, \omega = \Omega|_{r\rightarrow\infty}$,
and expand the solution to the leading order
\be
A_\phi = A_0 + a^2 A_2 , \quad \omega = a \omega_1 ,\quad i = a i_1.
\ee
Then we linearize the GS equation (\ref{eq:GSe}) as
\be
\mathcal L A_2(r,\theta) = S_2(r,\theta; i_1,\omega_1),
\ee
by only keeping leading order perturbation terms, where the source function $S_2$
depends on $i_1$ and $\omega_1$, which can be figured out from
the radiation conditions at  horizon and at infinity (\ref{eq:znajek}-\ref{eq:infty}).
The solution to the linearized GS equation is written as
\be
\begin{aligned}
A_2(r,\theta) =
\int\int dr_0  d\theta_0 \ S_2(r_0,\theta_0) G(r,\theta; r_0,\theta_0),
\end{aligned}
\ee
where $G(r,\theta; r_0,\theta_0)$ is the Green's function of operator $\mathcal L$ \citep{Petterson1974,Blandford1977}
\be
\mathcal LG(r,\theta; r_0,\theta_0) = \delta(r-r_0) \delta(\theta-\theta_0).
\ee
In this way, for a given Schwarzschild metric solution $A_0$, the corresponding
Kerr metric solution $\{A_\phi(a;,r,\theta), I(A_\phi),\Omega(A_\phi) \}$
is uniquely determined order by order.
Applying the method on the uniform field  problem $A_0=r^2\sst$, we find \citep{Beskin2013, Pan2014, Gralla2015},
\ben
\Omega = I = 0 && \quad (A_\phi > \AB), \\
\Omega = \frac{\WH}{2}\frac{\sqrt{1-A_\phi/\AB}}{1+\sqrt{1-A_\phi/\AB}}, && \ I=2\Omega A_\phi \quad (A_\phi < \AB).\nn
\een
where $\AB$ is the magnetic flux trapped by the event horizon
($\AB =4$ for the lowest-order perturbation solution, and generally depends on  BH spins and boundary conditions).

It seems that we have found the unique solution (at leading order) approaching uniform
field at infinity, but this is not the case.
The Schwarzschild spacetime GS equation (\ref{eq:lgs}) is linear.
Both uniform field and monopole field are its solutions, so do their linear combinations
\be
A_0(\epsilon) = r^2\sst + \epsilon (1-\ct),
\ee
where $\epsilon$ is some constant coefficient. The mixture of monopole component generates a
family of Schwarzschild metric solutions, $A_0(\epsilon)$, and all these solutions approach  uniform field at infinity.
For each solution, the corresponding Kerr metric solution $\{ A_\phi(\epsilon), I(\epsilon), \Omega(\epsilon) \}$
can be obtained using the above perturbation method.

To summarize, the perturbation method depends on two main ingredients:
the known asymptotic field behavior at infinity $A_\phi|_{r\rightarrow\infty}$
and the fixed underlying unperturbed field configuration $A_0$.
But for the uniform field problem,
there are many mathematically allowed unperturbed solutions
due to the additional monopole component.
That's why the perturbation approach cannot predict the unique solution.

\section{Summary and Discussions}
\label{sec:disc}
The GS equation is a second-order differential equation with two to-be-determined functions $\Omega$ and $I$.
Generally speaking, we need two constraint conditions to determine $\Omega$ and $I$,
two boundary conditions in the $r$ directions and two boundary conditions
in the $\mu$ direction to fix $A_\phi(r,\mu)$.
For asymptotically uniform field, we use constraint conditions (\ref{eq:ls},\ref{eq:constr}),
boundary conditions in the $r$ direction (\ref{eq:znajek},\ref{eq:rinfty})
and boundary conditions in the $\mu$ direction (\ref{eq:tbc}) to close the GS equation.
Our numerical solution of the uniform field yields a discontinuity in the $\Omega(A_\phi)$ at $\AB$,
therefore the ILS lies between the event horizon and the IRS, and there exists a current sheet along the last field
line crossing the event horizon (Figure \ref{fig:lines}), which is as expected from the horizon regularity condition.

Following the same logic, let us reexamine other two well studied field configurations:
monopole field in the Kerr spacetime and dipole field in the flat spacetime (classical pulsars).
For both field configurations, the number of LSs equals the number of to-be-determined functions $I$ and $\Omega$.
For monopole field in the Kerr spacetime, there are two LS crossing conditions and two radiation conditions.
The former two determine $\Omega$ and $I$, and the latter two determine the inner and the outer boundary.
Hence, there is no more freedom for specifying a boundary condition at infinity, i.e., we actually
do not know the solution at infinity before we really solve the GS equation.
Previous simulations and numerical solutions indeed confirmed
the asymptotic monopole field configuration $A_\phi \propto 1-\cos\theta$.
For pulsar dipole field, $\Omega$ is equal to the angular velocity of the central star
and $I$ is the only function to determine.
The only one LS uniquely determines $I$ \citep{Contopoulos1999},
and two radiation conditions automatically determine boundary conditions.
In the same way, there is no more freedom to impose a boundary
condition at infinity. And previous numerical studies found the field at infinity deviates from
$A_\phi \propto 1-\cos\theta$ \citep[e.g.][]{Gralla2016b}.

We also discuss the perturbation approach for solving the GS equation, whose
applicability depends on two main ingredients:
the known asymptotic field behavior at infinity $A_\phi|_{r\rightarrow\infty}$
and the fixed underlying unperturbed field configuration $A_0$.
For the monopole field, both of them are satisfied, therefore the perturbation approach
is applicable and the high-order perturbation solutions
show good match with results from simulations \citep{Pan2015b}.
For both uniform field in the Schwarzschild spacetime and dipole field surrounding static stars,
the superposition of monopole component (and possible other components) generates many unperturbed solutions,
as a result, the perturbation approach cannot predict
a unique uniform field solution in the Kerr spacetime or
a unique dipole field solution surrounding spinning stars.

\acknowledgements
We thank our referee Prof. I. Contopoulos for his insightful comments
on the validity of radiation condition for vertical field configurations and
on the possible difficulties arising form the discontinuity in the angular velocity of field lines.
We also thank A. Nathanail for clearly explaining his numerical algorithm.
C.Y. is grateful for the support by the National Natural Science Founda-
tion of China (grants 11173057, 11373064, 11521303),
Yunnan Natural Science Foundation (grants 2012FB187,
2014HB048), and the Youth Innovation Promotion Association, CAS.
Part of the computation was performed
at the HPC Center, Yunnan Observatories, CAS, China.
L.H. thanks the support by the National
Natural Science Foundation of China (grants 11203055).
This paper is supported in part by the Strategic Priority Research Program
``The Emergence of Cosmological Structures" of the Chinese Academy of Sciences,
grant No. XDB09000000 and Key Laboratory for Radio Astronomy, CAS.
This work made extensive use of the NASA Astrophysics Data System and
of the {\tt astro-ph} preprint archive at {\tt arXiv.org}.

%\bibliography{BZ}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{Alic {et~al.}(2012)Alic, Moesta, Rezzolla, Zanotti, \&
  Jaramillo}]{Alic2012}
Alic, D., Moesta, P., Rezzolla, L., Zanotti, O., \& Jaramillo, J. 2012,
  Astrophys. J., 754, 36

\bibitem[{Bambi(2012{\natexlab{a}})}]{Bambi2012b}
Bambi, C. 2012{\natexlab{a}}, Phys. Rev. D, 86, 123013

\bibitem[{Bambi(2012{\natexlab{b}})}]{Bambi2012}
---. 2012{\natexlab{b}}, Phys. Rev. D, 85, 043002

\bibitem[{Bambi(2015)}]{Bambi2015}
---. 2015, arXiv:1509.03884

\bibitem[{Begelman(1998)}]{Begelman1998}
Begelman, M.~C. 1998, Astrophys. J., 493, 291

\bibitem[{Beskin(2010)}]{Beskin2010}
Beskin, V.~S. 2010, Physics-Uspekhi, 53, 1199

\bibitem[{Beskin \& Zheltoukhov(2013)}]{Beskin2013}
Beskin, V.~S., \& Zheltoukhov, A.~A. 2013, Astron. Lett., 39, 215

\bibitem[{Blandford \& Znajek(1977)}]{Blandford1977}
Blandford, R.~D., \& Znajek, R.~L. 1977, Mon. Not. R. Astron. Soc., 179, 433

\bibitem[{Brennan {et~al.}(2013)Brennan, Gralla, \& Jacobson}]{Brennan2013}
Brennan, T.~D., Gralla, S.~E., \& Jacobson, T. 2013, Class. Quantum Gravity,
  30, 195012

\bibitem[{Comp{\`{e}}re {et~al.}(2016)Comp{\`{e}}re, Gralla, \&
  Lupsasca}]{Compere2016}
Comp{\`{e}}re, G., Gralla, S.~E., \& Lupsasca, A. 2016, arXiv:1606.06727

\bibitem[{Contopoulos {et~al.}(1999)Contopoulos, Kazanas, \&
  Fendt}]{Contopoulos1999}
Contopoulos, I., Kazanas, D., \& Fendt, C. 1999, Astrophys. J., 511, 351

\bibitem[{Contopoulos {et~al.}(2013)Contopoulos, Kazanas, \&
  Papadopoulos}]{Contopoulos2013}
Contopoulos, I., Kazanas, D., \& Papadopoulos, D. 2013, Astrophys. J., 765, 113

\bibitem[{Fendt(1997)}]{Fendt1997}
Fendt, C. 1997, Astron. Astrophys., 319, 1025

\bibitem[{Garofalo(2009)}]{Garofalo2009}
Garofalo, D. 2009, Astrophys. J., 699, 400

\bibitem[{Gralla \& Jacobson(2014)}]{Gralla2014}
Gralla, S.~E., \& Jacobson, T. 2014, Mon. Not. R. Astron. Soc., 445, 2500

\bibitem[{Gralla {et~al.}(2016{\natexlab{a}})Gralla, Lupsasca, \&
  Philippov}]{Gralla2016b}
Gralla, S.~E., Lupsasca, A., \& Philippov, A. 2016{\natexlab{a}},
  arXiv:1604.04625

\bibitem[{Gralla {et~al.}(2015)Gralla, Lupsasca, \& Rodriguez}]{Gralla2015}
Gralla, S.~E., Lupsasca, A., \& Rodriguez, M.~J. 2015, Phys. Rev. D, 92, 044053

\bibitem[{Gralla {et~al.}(2016{\natexlab{b}})Gralla, Lupsasca, \&
  Rodriguez}]{Gralla2016a}
---. 2016{\natexlab{b}}, Phys. Rev. D, 93, 044038

\bibitem[{Gruzinov(2005)}]{Gruzinov2005}
Gruzinov, A. 2005, Phys. Rev. Lett., 94, 021101

\bibitem[{Koide(2003)}]{Koide2003}
Koide, S. 2003, Phys. Rev. D, 67, 104010

\bibitem[{Koide \& Baba(2014)}]{Koide2014}
Koide, S., \& Baba, T. 2014, Astrophys. J., 792, 88

\bibitem[{Koide {et~al.}(2002)Koide, Shibata, Kudoh, \& Meier}]{Koide2002}
Koide, S., Shibata, K., Kudoh, T., \& Meier, D.~L. 2002, Science, 295, 1688

\bibitem[{Kojima(2015)}]{Kojima2015}
Kojima, Y. 2015, Mon. Not. R. Astron. Soc., 454, 3902

\bibitem[{Komissarov(2001)}]{Komissarov2001}
Komissarov, S. 2001, Mon. Not. R. Astron. Soc., 326, L41

\bibitem[{Komissarov(2004{\natexlab{a}})}]{Komissarov2004e}
---. 2004{\natexlab{a}}, Mon. Not. R. Astron. Soc., 350, 427

\bibitem[{Komissarov(2004{\natexlab{b}})}]{Komissarov2004}
---. 2004{\natexlab{b}}, Mon. Not. R. Astron. Soc., 350, 1431

\bibitem[{Komissarov(2005)}]{Komissarov2005}
---. 2005, Mon. Not. R. Astron. Soc., 359, 801

\bibitem[{Komissarov(2009)}]{Komissarov2009}
Komissarov, S.~S. 2009, J. Korean Phys. Soc., 54, 2503

\bibitem[{Komissarov \& McKinney(2007)}]{Komissarov2007}
Komissarov, S.~S., \& McKinney, J.~C. 2007, Mon. Not. R. Astron. Soc. Lett.,
  377, L49

\bibitem[{Lasota {et~al.}(2014)Lasota, Gourgoulhon, Abramowicz, Tchekhovskoy,
  \& Narayan}]{Lasota2014}
Lasota, J.-P., Gourgoulhon, E., Abramowicz, M., Tchekhovskoy, A., \& Narayan,
  R. 2014, Phys. Rev. D, 89, 024041

\bibitem[{Li(2000)}]{Li2000}
Li, L.-X. 2000, Astrophys. J. Lett., 531, L111

\bibitem[{Lyubarskii(1999)}]{Lyubarskii1999}
Lyubarskii, Y.~E. 1999, Mon. Not. R. Astron. Soc., 308, 1006

\bibitem[{McKinney(2005)}]{McKinney2005}
McKinney, J. 2005, Astrophys. J. Lett., 630, L5

\bibitem[{McKinney \& Blandford(2009)}]{McKinney2009a}
McKinney, J., \& Blandford, R. 2009, Mon. Not. R. Astron. Soc., 394, L126

\bibitem[{McKinney \& Gammie(2004)}]{McKinney2004}
McKinney, J., \& Gammie, C. 2004, Astrophys. J., 611, 977

\bibitem[{McKinney \& Narayan(2007{\natexlab{a}})}]{McKinney2007a}
McKinney, J.~C., \& Narayan, R. 2007{\natexlab{a}}, Mon. Not. R. Astron. Soc.,
  375, 513

\bibitem[{McKinney \& Narayan(2007{\natexlab{b}})}]{McKinney2007b}
---. 2007{\natexlab{b}}, Mon. Not. R. Astron. Soc., 375, 531

\bibitem[{McKinney {et~al.}(2013)McKinney, Tchekhovskoy, \&
  Blandford}]{McKinney2013}
McKinney, J.~C., Tchekhovskoy, A., \& Blandford, R.~D. 2013, Science, 339, 49

\bibitem[{Menon(2015)}]{Menon2015}
Menon, G. 2015, Phys. Rev. D, 024054, 024054

\bibitem[{Menon \& Dermer(2005)}]{Menon2005}
Menon, G., \& Dermer, C.~D. 2005, Astrophys. J., 635, 1197

\bibitem[{Menon \& Dermer(2007)}]{Menon2007}
---. 2007, Gen. Relativ. Gravit., 39, 785

\bibitem[{Menon \& Dermer(2011)}]{Menon2011}
---. 2011, Mon. Not. R. Astron. Soc., 417, 1098

\bibitem[{Nagataki(2009)}]{Nagataki2009}
Nagataki, S. 2009, Astrophys. J., 704, 937

\bibitem[{Nagataki(2011)}]{Nagataki2011}
---. 2011, \pasj, 63, 1243

\bibitem[{Narayan {et~al.}(2009)Narayan, Li, \& Tchekhovskoy}]{Narayan2009g}
Narayan, R., Li, J., \& Tchekhovskoy, A. 2009, Astrophys. J., 697, 1681

\bibitem[{Nathanail \& Contopoulos(2014)}]{Nathanail2014}
Nathanail, A., \& Contopoulos, I. 2014, Astrophys. J., 788, 186

\bibitem[{Palenzuela {et~al.}(2011)Palenzuela, Bona, Lehner, \&
  Reula}]{Palenzuela2011}
Palenzuela, C., Bona, C., Lehner, L., \& Reula, O. 2011, Class. Quantum
  Gravity, 28, 134007

\bibitem[{Palenzuela {et~al.}(2010)Palenzuela, Garrett, Lehner, \&
  Liebling}]{Palenzuela2010}
Palenzuela, C., Garrett, T., Lehner, L., \& Liebling, S.~L. 2010, Phys. Rev. D,
  82, 044045

\bibitem[{Pan \& Yu(2014)}]{Pan2014}
Pan, Z., \& Yu, C. 2014, arXiv:1406.4936

\bibitem[{Pan \& Yu(2015{\natexlab{a}})}]{Pan2015b}
---. 2015{\natexlab{a}}, Astrophys. J., 812, 57

\bibitem[{Pan \& Yu(2015{\natexlab{b}})}]{Pan2015}
---. 2015{\natexlab{b}}, Phys. Rev. D, 91, 064067

\bibitem[{Pan \& Yu(2016)}]{Pan2016}
---. 2016, Astrophys. J., 816, 77

\bibitem[{Pei {et~al.}(2016)Pei, Nampalliwar, Bambi, \& Middleton}]{Pei2016}
Pei, G., Nampalliwar, S., Bambi, C., \& Middleton, M.~J. 2016, Eur. Phys. J. C,
  76, 534

\bibitem[{Penna {et~al.}(2013)Penna, Narayan, \& Sadowski}]{Penna2013}
Penna, R., Narayan, R., \& Sadowski, A. 2013, Mon. Not. R. Astron. Soc., 436,
  3741

\bibitem[{Penna(2015)}]{Penna2015}
Penna, R.~F. 2015, Phys. Rev. D, 92, 084017

\bibitem[{Petterson(1974)}]{Petterson1974}
Petterson, J. 1974, Phys. Rev. D, 10, 3166

\bibitem[{Press {et~al.}(1987)Press, Teukolsky, Vetterling, Flannery, Ziegel,
  Press, Flannery, Teukolsky, \& Vetterling}]{Press1987}
Press, W., Teukolsky, S., Vetterling, W., {et~al.} 1987, {Numerical Recipes:
  The Art of Scientific Computing} (Cambridge University Press),
  doi:10.2307/1269484

\bibitem[{Scharlemann \& Wagoner(1973)}]{Scharlemann1973}
Scharlemann, E.~T., \& Wagoner, R.~V. 1973, Astrophys. J., 182, 951

\bibitem[{Semenov {et~al.}(2004)Semenov, Dyadechkin, \& Punsly}]{Semenov2004}
Semenov, V., Dyadechkin, S., \& Punsly, B. 2004, Science, 305, 978

\bibitem[{Takahashi {et~al.}(1990)Takahashi, Nitta, Tatematsu, \&
  Tomimatsu}]{Takahashi1990}
Takahashi, M., Nitta, S.-y., Tatematsu, Y., \& Tomimatsu, A. 1990, Astrophys.
  J., 363, 206

\bibitem[{Tanabe \& Nagataki(2008)}]{Tanabe2008}
Tanabe, K., \& Nagataki, S. 2008, Phys. Rev. D, 78, 024004

\bibitem[{Tchekhovskoy \& McKinney(2012)}]{Tchekhovskoy2012}
Tchekhovskoy, A., \& McKinney, J. 2012, Mon. Not. R. Astron. Soc., 423, L55

\bibitem[{Tchekhovskoy {et~al.}(2008)Tchekhovskoy, McKinney, \&
  Narayan}]{Tchekhovskoy2008}
Tchekhovskoy, A., McKinney, J.~C., \& Narayan, R. 2008, Mon. Not. R. Astron.
  Soc., 388, 551

\bibitem[{Tchekhovskoy {et~al.}(2010)Tchekhovskoy, Narayan, \&
  McKinney}]{Tchekhovskoy2010}
Tchekhovskoy, A., Narayan, R., \& McKinney, J. 2010, Astrophys. J., 711, 50

\bibitem[{Tchekhovskoy {et~al.}(2011)Tchekhovskoy, Narayan, \&
  McKinney}]{Tchekhovskoy2011}
---. 2011, Mon. Not. R. Astron. Soc., 418, L79

\bibitem[{Toma \& Takahara(2014)}]{Toma2014}
Toma, K., \& Takahara, F. 2014, Mon. Not. R. Astron. Soc., 442, 2855

\bibitem[{Toma \& Takahara(2016)}]{Toma2016}
---. 2016, Prog. Theor. Exp. Phys., 2016, arXiv:1605.03659

\bibitem[{Tomimatsu {et~al.}(2001)Tomimatsu, Matsuoka, \&
  Takahashi}]{Tomimatsu2001}
Tomimatsu, A., Matsuoka, T., \& Takahashi, M. 2001, Phys. Rev. D, 64, 123003

\bibitem[{Uzdensky(2004)}]{Udensky2004}
Uzdensky, D. 2004, Astrophys. J., 603, 652

\bibitem[{Uzdensky(2005)}]{Udensky2005}
---. 2005, Astrophys. J., 620, 889

\bibitem[{Wang {et~al.}(2004)Wang, Ma, Lei, \& Yao}]{Wang2004}
Wang, D., Ma, R., Lei, W., \& Yao, G. 2004, Astrophys. J., 601, 1031

\bibitem[{Yang \& Zhang(2014)}]{Yang2014}
Yang, H., \& Zhang, F. 2014, Phys. Rev. D, 90, 104022

\bibitem[{Yang {et~al.}(2015)Yang, Zhang, \& Lehner}]{Yang2015}
Yang, H., Zhang, F., \& Lehner, L. 2015, Phys. Rev. D, 91, 124055

\end{thebibliography}

\appendix
\label{sec:app}
For a given combination of $I(A_\phi)$ and $\Omega(A_\phi)$,
the horizon regularity condition (Equation (\ref{eq:znajek}))
uniquely determines the boundary condition at horizon $A_\phi(r= r_+, \mu)$.
We find its numerical solution is not trivial due to the nonlinearity.
To construct a robust solver, we first rewrite Equation (\ref{eq:znajek}) as
\be
    \mathcal I = \frac{2r(\Omega-\WH)\sst}{\Sigma} \mathcal A_{,\mu}\Big|_{r=r_+}
\ee
where we have defined two normalized variables, $\mathcal I = I / \AB$ and $\mathcal A = A_\phi / \AB$.
Here $\mathcal A $ runs from 0 to 1, and its values on boundaries are
$\mathcal A(\mu=0) = 1$ and $\mathcal A(\mu=1) = 0$.
Furthermore, we define $f(\mathcal A) \equiv \mathcal I/2(\WH - \Omega) $, and the above equation
is written in a variable separated form
\be
\frac{\mathcal A_{,\mu}}{f(\mathcal A)} = -\frac{r_+ \sst}{r_+^2 + a^2\mu^2},
\ee
which has a formal solution
\be
\label{eq:fs}
e^{\int_1^{\mathcal A(\mu)}\frac{d\mathcal A}{f(\mathcal A)}}
 = \frac{1-\mu}{1+\mu} \times e^{\frac{a^2}{r_+}\mu}.
\ee
In this form, numerically solving $\mathcal A(\mu)$ is stable.

Here we show a general property of force-free magnetospheres read out of the formal solution (\ref{eq:fs}):
the horizon condition requires the existence of a current sheet at the equator.
Enabling a non-singular solution, the integral $\int_1^{\mathcal A(\mu)}\frac{d\mathcal A}{f(\mathcal A)}$
must be finite, except at $\mathcal A = 0 (\mu = 1)$, where $f(\mathcal A) = 0$ due to vanishing $\mathcal I(\mu=1)$.
At $\mathcal A = 1 (\mu = 0)$, the finite integral requires nonzero $f(\mathcal A =1)$,
or quickly decreased $f(\mathcal A)$ (e.g., $\sim\sqrt{1-\mathcal A}$).
Usually $\Omega \leq \WH/2$, therefore $I(\AB)$ must be nonzero,
or quickly decrease to zero  (e.g., $\sim\sqrt{\AB-A_\phi}$), where the former is a current sheet at the equator,
and the later is a divergent current density (but weaker than the former).

\end{document}

### 2018-07-05 paper/ms.tex

@@
     the field lines entering the horizon. However,
-    recent high-accuracy general relativistic (GR) force-free electrodynamics (FFE) simulations \cite{East2018}
+    recent high-accuracy force-free electrodynamics (FFE) simulations \cite{East2018}
     show that there are both field lines entering the horizon and field lines ending up on
-    the equatorial current sheet
-    within the ergosphere for asymptotic uniform field configuration. For the latter, the equatorial boundary
+    the equatorial current sheet within the ergosphere for asymptotic uniform field configuration.
+    For the latter field lines, the equatorial boundary
     condition is well approximated being marginally force-free, i.e., $B^2-E^2\approx 0$, where $B$ and
@@
     line configuration and the source of the Poynting flux.
-    We also propose an algorithm for numerically solving the GR Grad-Shafranov equation and self-consistently imposing the marginally force-free equatorial
+    We also propose an algorithm for numerically solving the Grad-Shafranov equation and self-consistently imposing the marginally force-free equatorial
     condition. As a result, we find a good agreement between our numerical solutions and the high-accuracy FFE simulations.
-    We also discuss the applicability of the marginally force-free boundary condition and the numerical algorithm for general magnetic field configurations.
+    We also discuss the applicability of the marginally force-free boundary condition and the numerical algorithm
+    proposed in this paper for general magnetic field configurations.
 \end{abstract}
@@
 we have studied the BZ mechanism from different approaches and the cross-check among
-these different approaches has facilitate substantial progress in understanding the underlying
+these different approaches has facilitated substantial progress in understanding the underlying
 detailed physics. Taking the simple monopole magnetic field
@@
 different approaches do not even reach a consensus on the solution uniqueness for the uniform field configuration.
-Several force-free electrodynamics (FFE) simulation \cite{Komissarov2004e, Komissarov2005,
+Several force-free electrodynamics (FFE) simulations \cite{Komissarov2004e, Komissarov2005,
 Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017} have been done and
@@
 which is an indicator for solution uniqueness.
-However, a family of analytic solutions were presented for slowly spinning BHs,
-and no instability mode was found for any of these solutions \cite{Yang2015}. Therefore the solution stability
-is not likely the explanation for the solution uniqueness.
 
@@
 the two eigenfunctions. Following this argument, there should exist infinitely many solutions \cite{Nathanail2014}.
+In addition, a family of analytic solutions were presented for slowly spinning BHs,
+and no instability mode was found for any of these solutions \cite{Yang2015}. Therefore the solution stability
+is not likely the explanation for the solution uniqueness.
 
-To explain the discrepancy about the solution uniqueness from different approaches, Pan et.al. \cite{Pan2017}
-proposed that the two eigenfunctions are connected by the radiation condition at infinity instead of
-being independent, which was readily confirmed by recent FFE simulations done
+To explain the discrepancy about the solution uniqueness from different approaches, Pan et al.  \cite{Pan2017}
+proposed that the two eigenfunctions $\Omega(\Ap)$ and $I(\Ap)$ are connected by the radiation condition at infinity instead of
+being independent, which was readily confirmed by recent high-accuracy FFE simulations done
 by East and Yang \cite{East2018}. In addition, there are other interesting features in the structure of the BH
@@
 with the ergosphere, and the magnetic dominance marginally loses on the current sheet, i.e. $B^2-E^2\approx 0$.
-Motivated by these simulations, we revisit the uniform field solution and investigate the role of the
+
+Motivated by these simulation results, we revisit the uniform field solution and investigate the role of the
 marginally force-free equatorial boundary condition in the BH magnetosphere structure.
-We find the qualitative properties of the BH magnetosphere structure are attributed to the marginally
+We find the qualitative properties of the BH magnetosphere structure, including the shape of the LS,
+the near-horizon field line configuration, and the source of the Poynting flux, are attributed to the marginally
 force-free equatorial boundary condition without invoking the GS equation.
 We also  propose an algorithm for numerically solving the GS equation and
-consistently imposing the the marginally force-free equatorial boundary condition.
+self-consistently imposing the the marginally force-free equatorial boundary condition.
 As a result, we find our numerical solutions are in good agreement with the FFE simulations.
@@
 The paper is organized as follows.  In Section \ref{sec:basic}, we outline the basic governing equations.
-In Section \ref{sec:uni_sol}, we clarify the radiation condition, boundary conditions and numerical algorithm
+In Section \ref{sec:uni_sol}, we clarify the radiation condition, boundary conditions and the numerical algorithm
 for the uniform field solution. In Section \ref{sec:discussion}, we generalize the discussion
@@
 -\frac{4ra}{\Sigma}\Omega \sst
--\left(1-\frac{2r}{\Sigma}\right)\right,
+-\left(1-\frac{2r}{\Sigma}\right),
 \ee
@@
 the LS function vanishes and the GS equation degrades from second order to first order. As proposed
-by Contopoulos et.al. \cite{Contopoulos2013}, one can adjust the two eigenfunctions $\Omega(\Ap)$
+by Contopoulos et al. \cite{Contopoulos2013}, one can adjust the two eigenfunctions $\Omega(\Ap)$
 and $I(\Ap)$ enabling field lines smoothly cross the two LSs, then the solution
-$\{\Omega(\Ap), I(\Ap), \Ap(r,\theta)\}$  is uniquely found. But for the vertical field lines, their
+$\{\Omega(\Ap), I(\Ap), \Ap(r,\theta)\}$  is uniquely ensured. But for the vertical field lines, their
 exists only one LS, which is insufficient for determining two eigenfunctions.
-Therefore many solutions are expected \cite{Nathanail2014, Mahlmann2018}, but the many-solutions scenario is in
+In this case, many solutions are expected \cite{Nathanail2014, Mahlmann2018}, but the many-solutions scenario is in
 conflict with several previous FFE simulations \cite{Komissarov2004e, Komissarov2005,
 Komissarov2007,Palenzuela2010,Paschalidis2013,Yang2015,Carrasco2017}.
-To tackle this problem,  Pan et. al. \cite{Pan2016a, Pan2017} proposed that the two eigenfunctions are not independent;
+To explain the discrepancy on the uniqueness of uniform field solution,
+Pan et al. \cite{Pan2016a, Pan2017} proposed that the two eigenfunctions are not independent;
 instead, they are related by the radiation condition at infinity
@@
 where $r_+$ is the radius of the event horizon,
-while the equatorial boundary condition is more uncertain until recent simulations \cite{East2018}
-come out which show that there exists an equator current sheet within the ergosphere where the
-magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$. Motivated by the simulation results,
+while the equatorial boundary condition is more uncertain until recent high-accuracy simulations
+come out showing that there exists an equator current sheet within the ergosphere where the
+magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$ \cite{East2018}. Motivated by the simulation results,
 we choose the following equatorial boundary condition in our numerical solutions,
@@
 From the expression of the LS function (\ref{eq:ls}), it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
-On this point,  the LS function $\mathcal K$ vanishes,
+At this point,  the LS function $\mathcal K$ vanishes,
 and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
@@
 
-From above analysis, we expect several generic features in the magnetospheres that are independent
+From above analysis, we expect several generic properties in the magnetospheres that are independent
 of the GS equation:
-(1) the LS runs from $r=r_+$ to $r=2$ as $\theta$ varies from $0$ to $\pi/2$,
+(1) the LS runs from $r=r_+$ to $r=2$ as $\theta$ varies from $0$ to $\pi/2$;
 (2) since $I$ vanishes at $r_{\rm LS}|_{\mu=0}$, we expect no current sheet within the magnetosphere except the equatorial current
-sheet extending from $r_+$ to $2$, which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines,
+sheet extending from $r_+$ to $2$, which gives rise to a cusp ($\Am \neq 0$) to the equatorial magnetic field lines;
 (3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
@@
 nor guarantees the boundary condition (\ref{eq:bc3}). We  adjust
-$\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
+$\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows,
 \be
@@
 In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
-which explicitly displays the features we anticipated in Section \ref{subsec:features} and agrees with
+which explicitly displays the properties we anticipated in Section \ref{subsec:features} and agrees with
 the simulation results in detail \cite{East2018}.
@@
 Lower Panel: comparison of our numerical results (solid lines) with the simulation results of
-Ref.\cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
+Ref. \cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
 dash-dotted lines.}
@@
 To summarize, the uniform field solution is indeed unique as double confirmed by the high-accuracy FFE
-simulations and by our numerical solutions, where the radiation condition and the marginally force-free
-equatorial boundary condition largely shape the  structure of the BH magnetosphere.
+simulations and by our numerical solutions. The  structure of the BH magnetosphere
+is largely shaped by the radiation condition and the marginally force-free
+equatorial boundary condition.
 
@@
 simplification obviously misses magnetic field lines rooting on the
-equatorial current sheet, which contribute about half of the total BZ flux for extremal spins in
+equatorial current sheet, which contribute about half of the total Poynting flux for extremal spins in
 the case of uniform field configuration.
@@
 condition (\ref{eq:bc3}) should also be a good work approximation for studying
-the BH magnetosphere structure with parabolic magnetic field lines.
+the BH magnetosphere embedded in parabolic magnetic field lines.
 It is straightforward to solve the GS equation and self-consistently
@@
 where the function $\mathcal F(\Ap)$ is of $\mathcal O(\Ap)$ and  is field configuration dependent.
-The basic logic for obtaining the claim is as follows.
-$\Omega$ must be nonzero for all field lines entering the ergosphere due to the frame-dragging effect;
+The basic logic for obtaining the claim above is as follows.
+The angular velocity $\Omega$ must be nonzero for all field lines entering the ergosphere due to the frame-dragging effect;
 as a result, $I$ must be nonzero for these field lines according to the radiation condition.
-If there is field line entering the ergosphere and crossing the equator, the electric current either flows
+If there is a field line entering the ergosphere and crossing the equator, the electric current either flows
 towards the equator from both the $+z$ and $-z$ side, or flows away from the equator to infinity in
@@
 
-However, the FFE simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
+However, the high-accuracy FFE simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
 the force-free condition breaks down. Therefore the above claim should be generalized as
@@
 instead of being independent \cite{Pan2017}, which was readily confirmed by recent high-accuracy
-FFE simulations \cite{East2018}. In these simulations, an equatorial current sheet
-develops within the ergosphere and the magnetic dominance marginally loses, i.e. $B^2-E^2\approx 0$.
+FFE simulations \cite{East2018}. In addition, these simulations also provide a close look at the
+equatorial boundary condition: an equatorial current sheet develops within the ergosphere and the magnetic dominance marginally loses, i.e. $B^2-E^2\approx 0$.
 
-Motivated by these simulations, we revisit the problem of the uniform field solution in this paper.
+Motivated by these simulation results, we revisit the problem of the uniform field solution in this paper.
 We find the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
@@
 In realistic astrophysical environment, we expect the magnetic field lines far away from the central BH
-are more close to parabolas instead of being strictly vertical. However, we also expect the marginally
-force-free equatorial boundary condition to be a good working approximation for the parabolic field configurations,
+are more close to be parabolic instead of being strictly vertical. However, we also expect the marginally
+force-free equatorial boundary condition to be a good working approximation for studying the parabolic field configurations,
 due to the resemblance of the near-horizon field configurations in the two cases.
@@
 \acknowledgements
+ZP thanks ...
 ZP was supported by the UC Davis Dissertation Year Fellowship when this work was started.

### 2018-07-06 scripts/SOR.jl
save

@@ -86,9 +86,9 @@ function BC_gen(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I; BC_op
         iip  = Ispl(Ucol).*derivative(Ispl, Ucol)
         IIp  = Ω_I.IIpspl(Ucol)
 
-        Ueqt, B2mE2 = Fsq_only(U, crd, grd, Ω_I)
+        Ueqt, δ_B2mE2 = Fsq_only(U, crd, grd, Ω_I)
 
-        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip) - Isf_BE*(1.-rcol/rcol[end]).*B2mE2
+        ∂μUnew  = ∂μU[1:idx_r2] + Isf*(IIp-iip) - Isf_BE*(1.-rcol/rcol[end]).*δ_B2mE2
         pmodel(x, p) = ( p[1] + p[2] .* x + p[3] .* x.^2 + p[4] .* x.^3 + p[5] .* x.^4 + p[6] .* x.^5 )
         pfit   = curve_fit(pmodel, rcol, ∂μUnew, [0., 0., 0., 0., 0., 0.])
         ∂μU[1:idx_r2] = pmodel(rcol, pfit.param)

### 2018-07-06 scripts/func.jl

@@ -120,17 +120,17 @@ end
 function Ωpar_updater!(U::Array{Float64,2}, crd::Cord, grd::Grid, Ω_I::Ω_and_I, ils::LS; Isf = 0.02)
     Ucol = reverse(ils.ULS); U_H =  Ucol[end]
 
-    Ueqt, B2mE2, B2mE2_exp, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
-    Icrt_spl  = Spline1D(Ueqt[2:end], B2mE2[2:end], bc="zero")
-    I_eqt = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt_spl(Ucol)
-    I_hrz = Ω_I.Ispl(Ucol)
-    I_new = I_hrz.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1]) + I_eqt.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1])
+    Ueqt, δ_B2mE2, fsq, fsq2_avg = Fsq(U, crd, grd, Ω_I)
+    Icrt_spl  = Spline1D(Ueqt[2:end], δ_B2mE2[2:end], bc="zero")
+    I_eqt     = 2*Ω_I.Ωspl(Ucol).*Ucol - Isf*Icrt_spl(Ucol)
+    I_hrz     = Ω_I.Ispl(Ucol)
+    I_new     = I_hrz.*(Ucol[end] -Ucol)/(Ucol[end]-Ucol[1]) + I_eqt.*(Ucol-Ucol[1])/(Ucol[end]-Ucol[1])
 
     xcol = Ucol/U_H;  Ω_H  = crd.Ω_H
     Ωmodel(x, p) = Ω_H.*(1-x).*(0.5+p[1]*x + p[2]*x.^2 + p[3]*x.^3 + p[4]*x.^4)
     Imodel(x, p) = 2*(U_H*x).*(  Ω_H.*(1-x).*(0.5+p[1]*x + p[2]*x.^2 + p[3]*x.^3 + p[4]*x.^4) )
-    Ifit = curve_fit(Imodel, xcol, I_new, [0., 0., 0., 0.])
-    Ωnew = Ωmodel(xcol, Ifit.param)
+    Ifit         = curve_fit(Imodel, xcol, I_new, [0., 0., 0., 0.])
+    Ωnew         = Ωmodel(xcol, Ifit.param)
     return Ifit.param, fsq2_avg
 end
 
[…]

### 2018-07-06 scripts/run.jl

@@ -45,7 +45,7 @@ while (Ωpar_loop <= 15) & (fsq2_avg > 2.e-4)
     Ω_par, fsq2_avg =  Ωpar_updater!(U, crd, grd, Ω_I, ils, Isf = 0.06)
     Ωpar_loop +=1
     println("fsq2_avg = $fsq2_avg")
-    @save "/home/zhenpan/Astroph/Uniform_Sol/scripts/a$(crd.a).jld" Ωpar_loop crd mtr Ω_par U Ω_I U_H grd ils lsn δU bc_eqt fsq2_avg
+    @save "/home/zhenpan/Astroph/Uniform_Sol/scripts/a$(crd.a)_test.jld" Ωpar_loop crd mtr Ω_par U Ω_I U_H grd ils lsn δU bc_eqt fsq2_avg
 end
 
 
@@ -73,7 +73,7 @@ include("scripts/func.jl")
 
 δU = zeros(crd.μlen); Res = 0.
 
-while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
+while (Ωpar_loop <= 45) & (fsq2_avg > 1.e-4)
     for BCloop = 1:15
         for Ωloop = 1:150
             for Iloop = 1:5
@@ -88,7 +88,7 @@ while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
             ils, Ω_I = LS_updater!(U, grd, crd, Ω_I, ils, Ω_par)     #update ils and Ω_I.Ωspl from (ils.ULS, ils.Ω)
             lsn      = LS_neighbors(U, ils, grd, crd)
         end
-            ISF_BE   = Ωpar_loop > 10 ? 0.1:0.
+            ISF_BE   = Ωpar_loop > 10 ? 0.2:0.
             bc_eqt   = BC_gen(U, crd, grd, Ω_I, BC_opt = 1, Isf = 6.0, Isf_BE = ISF_BE)
             Ubm = linspace(0., U_H, 64)
             plot(Ubm, Ω_I.Ωspl(Ubm))
@@ -105,6 +105,7 @@ while (Ωpar_loop <= 20) & (fsq2_avg > 2.e-4)
     println("fsq2_avg = $fsq2_avg")
     @save "/home/zhenpan/Astroph/Uniform_Sol/scripts/a$(crd.a).jld" Ωpar_loop crd mtr Ω_par U Ω_I U_H grd ils lsn δU bc_eqt fsq2_avg
 end
+
 
 
 ###############################################################################

### 2018-07-06 paper/ms.tex
save

@@
 to  more field configurations. Summary is given in Section \ref{sec:summary}.
+Throughout this paper, we use the convention $G=c=M=1$ if otherwise specified,
+where $M$ the mass of the BH.
 
@@
 \]
-where $\Sigma = r^2 + a^2 \mu^2$, $\Delta = r^2 -2r + a^2$,
+where $\mu\equiv\ct$, $\Sigma = r^2 + a^2 \mu^2$, $\Delta = r^2 -2r + a^2$,
 $\beta = \Delta\Sigma + 2r(r^2 + a^2)$, and $a$ is the dimensionless BH spin.
@@
 \ee
-$\mu\equiv\ct$,  and  the primes designate  derivatives with respect to $A_\phi$.
+the primes designate  derivatives with respect to $A_\phi$.
 $\partial_i^\Omega (i=r, \mu)$  denotes the partial derivative
@@
 come out showing that there exists an equator current sheet within the ergosphere where the
-magnetic dominance marginally loses, i.e., $B^2-E^2\approx 0$ \cite{East2018}. Motivated by the simulation results,
+magnetic dominance marginally loses, i.e., $(B^2-E^2)/B_0^2$ goes to a small positive value
+as approaching the current sheet, where $B_0$ is the uniform field strength at infinity  \cite{East2018}. Motivated by the simulation results,
 we choose the following equatorial boundary condition in our numerical solutions,
@@
 while the angular velocity $\Omega$ as a function
-of normalized magnetic flux $\Ap/\AEE$ is in agreement with the simulation results to high precision.
+of normalized magnetic flux $\Ap/\AEE$ is in agreement with the
+simulation results to high precision.\footnote{We have done a test and
+find that the $\approx 5\%$ difference in $\AEE$ is not arising from the slightly
+different equatorial boundary conditions used in this work and found from East and Yang's simulations.
+The difference is more likely due to the relative bias between the two codes. }
 
@@
 \acknowledgements
-ZP thanks ...
+ZP thanks William East and Huan Yang for sharing their simulation results,
+and for stimulating discussions.
 ZP was supported by the UC Davis Dissertation Year Fellowship when this work was started.

### 2018-07-06 paper/ms.tex
done

@@
 to  more field configurations. Summary is given in Section \ref{sec:summary}.
-Throughout this paper, we use the convention $G=c=M=1$ if otherwise specified,
+Throughout this paper, we use the convention $G=c=M=1$ only if otherwise specified,
 where $M$ the mass of the BH.
@@
 \acknowledgements
-ZP thanks William East and Huan Yang for sharing their simulation results,
-and for stimulating discussions.
+ZP thanks William East and Huan Yang for stimulating discussions and for sharing their simulation results.
 ZP was supported by the UC Davis Dissertation Year Fellowship when this work was started.

### 2018-07-12 paper/ms.tex
final

@@
 magnetic dominance marginally loses, i.e., $(B^2-E^2)/B_0^2$ goes to a small positive value
-as approaching the current sheet, where $B_0$ is the uniform field strength at infinity  \cite{East2018}. Motivated by the simulation results,
+as approaching the current sheet, where $B_0$ is the uniform field strength
+at infinity  \cite{East2018}.\footnote{The marginally force-free equatorial boundary condition
+is not a unique feature of BH magnetospheres, which is also found in dissipative pulsar magnetospheres
+\cite[see e.g.][]{Gruzinov2008, Gruzinov2011}.}
+Motivated by the simulation results,
 we choose the following equatorial boundary condition in our numerical solutions,
@@
 different equatorial boundary conditions used in this work and found from East and Yang's simulations.
-The difference is more likely due to the relative bias between the two codes. }
+The difference is more likely due to the relative numerical bias between the two algorithms. }
 
@@
 
-In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$
+In Figure \ref{fig:Edot}, we compare the energy extraction rates $\dot E(\WH)$
 derived from our numerical solutions with East and Yang's simulation results
@@
 However, the high-accuracy FFE simulations show that an equatorial current sheet inevitably develops within the ergosphere, where
-the force-free condition breaks down. Therefore the above claim should be generalized as
+the force-free condition marginally breaks down. Therefore the above claim should be generalized as
 ``in the steady axisymmetric force-free magnetosphere
@@
 \acknowledgements
-ZP thanks William East and Huan Yang for stimulating discussions and for sharing their simulation results.
+ZP thanks William East and Huan Yang for stimulating discussions and sharing their simulation results.
+ZP also thanks Cong Yu and Lei Huang for reading through a previous version of this manuscript and providing useful suggestions.
 ZP was supported by the UC Davis Dissertation Year Fellowship when this work was started.

### 2018-07-17 paper/ms.tex
xx

@@
 (3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
-both of which carry electric current and therefore Poynting flux.
+both of which carry electric current and therefore Poynting flux (see \cite{Punsly1990} for a physical realization of
+equatorial current sheet sourcing Poynting flux).
 

### 2018-08-19 paper/ms.tex
reply to referee

@@
 with respect to coordinate $i$ with $\Omega$ fixed, and $\partial_\Omega$ is the derivative with
-respect to $\Omega$.
+respect to $\Omega$. {\bf The GS equation degrades to first order on the LS, where $\mathcal K(r,\theta; \Omega )$ vanishes.}
 
@@
 Pan et al. \cite{Pan2016a, Pan2017} proposed that the two eigenfunctions are not independent;
-instead, they are related by the radiation condition at infinity
+instead, they are related by the radiation condition at infinity, {\bf which is formulated as
+$\hat E_\theta = \hat B_\phi$, with $\hat E_\theta$ and $\hat B_\phi$ being the $\theta$
+component of electric field and $\phi$ component of the magnetic field measured by zero-angular-momentum-observers, respectively.
+As for the uniform field solution, the radiation condition is explicitly expressed as }
 \be I = 2\Omega A_\phi, \label{eq:rad}\ee
@@
 \begin{aligned}
-&B^2-E^2 \\
+&B^2-E^2 \label{eq:B2mE2}\\
 = & \frac{1}{\Sigma \sst} \left[ -\mathcal{K} \left(\Ar^2 +\frac{\sst}{\Delta}\Am^2 \right)+\frac{\Sigma}{\Delta}I^2\right],
@@
 Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
-From the expression of the LS function (\ref{eq:ls}), it is straightforward to see $ r_{\rm LS}|_{\mu=0} \leq 2$ for $\Omega \geq 0$.
-At this point,  the LS function $\mathcal K$ vanishes,
+{\bf On this point $r_{\rm LS}|_{\mu=0}$,  the LS function $\mathcal K$ vanishes,
 and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
 which in turns indicates a vanishing angular velocity $\Omega$ from
-the radiation condition (\ref{eq:rad}).  Due to the frame-dragging effect, $\Omega$
-must be non-zero inside the ergosphere.  Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$, i.e.
+the radiation condition (\ref{eq:rad}), i.e. $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$. 
+Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ into $\mathcal K = 0$,
+we obtain $r_{\rm LS}|_{\mu=0}=2$. i.e.
 to satisfy the boundary condition (\ref{eq:bc3}), the LS must intersect the equator at $r=2$, which also
-justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) .
+justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) . }
+% From the expression of the LS function (\ref{eq:ls}), it is straightforward to see
+% $ r_+ \leq r_{\rm LS}|_{\mu=0} \leq 2$ for $0 \leq \Omega \leq \Omega_{\rm H}$.
+%  Due to the frame-dragging effect, $\Omega$
+% must be non-zero inside the ergosphere.
+%Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$,
 

### 2018-08-19 paper/reply.tex
reply

\documentclass[10pt]{article}
\usepackage{color}
\usepackage[top = 20mm, bottom= 25mm]{geometry}
\usepackage{enumerate}
\usepackage{amsmath,amssymb, amsthm,amstext}

\parskip=2mm
\parindent=5mm
\textwidth=170mm
%\textheight=250mm
\oddsidemargin= -5mm
\evensidemargin= -5mm

\def \Pan {{\bf Z. Pan}}
\def \Font{\tt}
\def \JFont{\tt}

\begin{document}
%\newpage
%\pagestyle{empty}

\begin{center}
{{\large\bf Reply to Referee Report -- DU12480/Pan}}
\end{center}

\begin{center}
{\normalsize Zhen Pan}
\end{center}

I thank the referee for  careful reading of this manuscript and
giving insightful comments. I summarize our corrections/clarifications as follows,
and all important modifications in the manuscript are highlighted in bold font.\\

{\bf The author discusses the role of boundary conditions (at infinity and at the equator) in black hole forcefree
magnetospheres. This clarifies a few aspects of the problem and is worthy of publication.
However, I have some concerns I would like to first see addressed:

1) There should be more discussion of the physical meaning of the “radiation condition” (3). What
is the relationship to radiation, and what does it mean? }

Pan et al.  proposed that the two eigenfunctions are not independent;
instead, they are related by the radiation condition at infinity, which is formulated as
$\hat E_\theta = \hat B_\phi$, with $\hat E_\theta$ and $\hat B_\phi$ being the $\theta$
component of electric field and $\phi$ component of the magnetic field measured
by zero-angular-momentum-observers, respectively.
As for the uniform field solution, the radiation condition is explicitly expressed as
\[ I = 2\Omega A_\phi, \]
which has been readily confirmed by recent high-accuracy FFE simulations (East2018).

{\bf 2) The notion of a light surface (LS) is not defined anywhere, as far as I can tell. Also, it would help
to state the meaning of the LS function (it vanishes at LS’s) right when it is defined.}

{\bf 3) The argument for the LS intersecting the ergosphere boundary on the equator needs
clarification. I found it hard to follow, and I was easily able to find a counter-example to the first
statement (a=.1, Omega=.15; there are two zeros of K on the equator, both at r>2). }

{\bf Finally, a suggestion:
• The proof that the inner light cylinder intersects the ergosphere boundary at the equator is
a very nice result (assuming it is correct). A few groups have seen that the current sheet
ends at the ergosphere in full simulations but people seem sheepish about making the claim
because of numerical resolution. The analytical argument is a big help here, so the author
might consider emphasizing the point more somehow.}

We thank the referee for comments that we feel have .

\end{document}

### 2018-08-19 paper/ms.tex
done

@@
 Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
-{\bf On this point $r_{\rm LS}|_{\mu=0}$,  the LS function $\mathcal K$ vanishes,
-and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
+{\bf On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
+$I$ must also vanish for satisfying the marginally boundary condition (see Equation [\ref{eq:B2mE2}]),
 which in turns indicates a vanishing angular velocity $\Omega$ from
-the radiation condition (\ref{eq:rad}), i.e. $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$. 
-Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ into $\mathcal K = 0$,
+the radiation condition (\ref{eq:rad}), i.e., $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$.
+Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
 we obtain $r_{\rm LS}|_{\mu=0}=2$. i.e.
@@
 justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) . }
-% From the expression of the LS function (\ref{eq:ls}), it is straightforward to see
-% $ r_+ \leq r_{\rm LS}|_{\mu=0} \leq 2$ for $0 \leq \Omega \leq \Omega_{\rm H}$.
-%  Due to the frame-dragging effect, $\Omega$
-% must be non-zero inside the ergosphere.
-%Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$,
 
@@
 in various aspects, including the shape of the LS, the near-horizon field line configuration and
-the source of BZ flux (see Section \ref{subsec:features} for details). Other than these qualitative properties,
+the source of BZ flux (see Section \ref{subsec:features} for details). {\bf Especially we find the LS
+intersects with the ergosphere at the equator, which was also observed in previous simulations \cite[e.g.][]{Carrasco2017, East2018}
+and now we understand its underlying physics.}
+Other than these qualitative properties,
 we also propose an algorithm for numerically solving the GS equation and consistently imposing

### 2018-08-19 paper/reply.tex
done

@@
 
-Pan et al.  proposed that the two eigenfunctions are not independent;
+To give more information about the radiation condition, I revise the relevant statement as follows:
+
+``Pan et al.  proposed that the two eigenfunctions are not independent;
 instead, they are related by the radiation condition at infinity, which is formulated as
@@
 \[ I = 2\Omega A_\phi, \]
-which has been readily confirmed by recent high-accuracy FFE simulations (East2018).
+which has been readily confirmed by recent high-accuracy FFE simulations. " \\
 
@@
 
+To clarify the definition of LS, I have added a sentence following the LS function formula:
+
+``The GS equation degrades to first order on the LS, where $\mathcal K(r,\theta; \Omega )$
+vanishes. " \\
+
 {\bf 3) The argument for the LS intersecting the ergosphere boundary on the equator needs
 clarification. I found it hard to follow, and I was easily able to find a counter-example to the first
-statement (a=.1, Omega=.15; there are two zeros of K on the equator, both at r>2). }
+statement (a=.1, Omega=.15; there are two zeros of K on the equator, both at $r>2$). }
+
+The referee's comment makes me realize the problem of the original argument, which I have reorginized as follows:
+
+``Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
+On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
+$I$ must also vanish for satisfying the marginally boundary condition (see Equation [6]),
+which in turns indicates a vanishing angular velocity $\Omega$ from
+the radiation condition (3), i.e. $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$.
+Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
+we obtain $r_{\rm LS}|_{\mu=0}=2$"
 
 {\bf Finally, a suggestion:
-• The proof that the inner light cylinder intersects the ergosphere boundary at the equator is
+The proof that the inner light cylinder intersects the ergosphere boundary at the equator is
 a very nice result (assuming it is correct). A few groups have seen that the current sheet
@@
 
-We thank the referee for comments that we feel have .
+To emphasize this point, I have added a sentence in the Summary:
+
+``Especially we find the LS
+intersects with the ergosphere at the equator, which was also observed in previous simulations
+[e.g. Carrasco2017, East2018] and now we understand its underlying physics. "
 

### 2018-08-20 paper/ms.tex
final version

@@
 to  more field configurations. Summary is given in Section \ref{sec:summary}.
-Throughout this paper, we use the convention $G=c=M=1$ only if otherwise specified,
+Throughout this paper, we use the convention $G=c=M=1$ unless otherwise specified,
 where $M$ the mass of the BH.
@@
 with respect to coordinate $i$ with $\Omega$ fixed, and $\partial_\Omega$ is the derivative with
-respect to $\Omega$. {\bf The GS equation degrades to first order on the LS, where $\mathcal K(r,\theta; \Omega )$ vanishes.}
+respect to $\Omega$. {\bf The GS equation degrades to first order on the LS,
+where the LS function $\mathcal K(r,\theta; \Omega )$ vanishes.}
 
@@
 {\bf On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
-$I$ must also vanish for satisfying the marginally boundary condition (see Equation [\ref{eq:B2mE2}]),
+$I$ must also vanish for satisfying the marginally force-free boundary condition (see Equation [\ref{eq:B2mE2}]),
 which in turns indicates a vanishing angular velocity $\Omega$ from
@@
 Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
-we obtain $r_{\rm LS}|_{\mu=0}=2$. i.e.
+we obtain $r_{\rm LS}|_{\mu=0}=2$, i.e.
 to satisfy the boundary condition (\ref{eq:bc3}), the LS must intersect the equator at $r=2$, which also
@@
 intersects with the ergosphere at the equator, which was also observed in previous simulations \cite[e.g.][]{Carrasco2017, East2018}
-and now we understand its underlying physics.}
+and now we understand its underlying physics: the radiation condition and the marginally force-free condition.}
 Other than these qualitative properties,

### 2018-08-20 paper/reply.tex
final version

@@
 I thank the referee for  careful reading of this manuscript and
-giving insightful comments. I summarize our corrections/clarifications as follows,
+giving insightful comments, which I feel have led to important improvements in
+the paper clarity.
+I summarize the corrections/clarifications as follows,
 and all important modifications in the manuscript are highlighted in bold font.\\
@@
 
-``Pan et al.  proposed that the two eigenfunctions are not independent;
+``Pan et al. [23,24]  proposed that the two eigenfunctions are not independent;
 instead, they are related by the radiation condition at infinity, which is formulated as
@@
 \[ I = 2\Omega A_\phi, \]
-which has been readily confirmed by recent high-accuracy FFE simulations. " \\
+which has been readily confirmed by recent high-accuracy FFE simulations [1]. " \\
 
@@
 
-To clarify the definition of LS, I have added a sentence following the LS function formula:
+To clarify the definition of LS and the meaning of the LS function, I have added a sentence following the LS function formula:
 
-``The GS equation degrades to first order on the LS, where $\mathcal K(r,\theta; \Omega )$
+``The GS equation degrades to first order on the LS, where the LS function $\mathcal K(r,\theta; \Omega )$
 vanishes. " \\
@@
 
-The referee's comment makes me realize the problem of the original argument, which I have reorginized as follows:
+The referee's comment makes me realize the vagueness of the original argument, which I have reorginized as follows:
 
@@
 On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
-$I$ must also vanish for satisfying the marginally boundary condition (see Equation [6]),
+$I$ must also vanish for satisfying the marginally force-free boundary condition (see Equation [6]),
 which in turns indicates a vanishing angular velocity $\Omega$ from
@@
 Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
-we obtain $r_{\rm LS}|_{\mu=0}=2$"
+we obtain $r_{\rm LS}|_{\mu=0}=2$" \\
 
@@
 intersects with the ergosphere at the equator, which was also observed in previous simulations
-[e.g. Carrasco2017, East2018] and now we understand its underlying physics. "
+[e.g. Carrasco2017, East2018] and now we understand its underlying physics:
+the radiation condition and the marginally force-free condition. "
 

### 2018-09-23 paper/ms.tex
rm grammer errs

@@
 \begin{document}
-\title{The magnetosphere structure of a Kerr black hole:
+\title{Magnetosphere structure of a Kerr black hole:
 marginally force-free equatorial boundary condition}
@@
     a force-free black hole magnetosphere was rarely discussed, since previous studies have been focused on the
-    the field lines entering the horizon. However,
+    field lines entering the horizon. However,
     recent high-accuracy force-free electrodynamics (FFE) simulations \cite{East2018}
